### 2018-09-26 paper.tex
Stub for real paper

\documentclass{article}

\usepackage{microtype}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{booktabs}
\usepackage{hyperref}

% Attempt to make hyperref and algorithmic work together better:
\newcommand{\theHalgorithm}{\arabic{algorithm}}

% Use the following line for the initial blind version submitted for review:
\usepackage{sysml2019}

% If accepted, instead use the following line for the camera-ready submission:
%\usepackage[accepted]{sysml2019}

% The \sysmltitle you define below is probably too long as a header.
% Therefore, a short form for the running title is supplied here:
\sysmltitlerunning{Submission and Formatting Instructions for SysML 2019}

\begin{document}

\twocolumn[
\sysmltitle{Submission and Formatting Instructions for SysML 2019}

% It is OKAY to include author information, even for blind
% submissions: the style file will automatically remove it for you
% unless you've provided the [accepted] option to the sysml2019
% package.

% List of affiliations: The first argument should be a (short)
% identifier you will use later to specify author affiliations
% Academic affiliations should list Department, University, City, Region, Country
% Industry affiliations should list Company, City, Region, Country

% You can specify symbols, otherwise they are numbered in order.
% Ideally, you should not use this facility. Affiliations will be numbered
% in order of appearance and this is the preferred way.
\sysmlsetsymbol{equal}{*}

\begin{sysmlauthorlist}
\sysmlauthor{Aeiau Zzzz}{equal,to}
\sysmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
\sysmlauthor{Cieua Vvvvv}{goo}
\sysmlauthor{Iaesut Saoeu}{ed}
\sysmlauthor{Fiuea Rrrr}{to}
\sysmlauthor{Tateu H.~Yasehe}{ed,to,goo}
\sysmlauthor{Aaoeu Iasoh}{goo}
\sysmlauthor{Buiui Eueu}{ed}
\sysmlauthor{Aeuia Zzzz}{ed}
\sysmlauthor{Bieea C.~Yyyy}{to,goo}
\sysmlauthor{Teoau Xxxx}{ed}
\sysmlauthor{Eee Pppp}{ed}
\end{sysmlauthorlist}

\sysmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
\sysmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
\sysmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}

\sysmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
\sysmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}

% You may provide any keywords that you
% find helpful for describing your paper; these are used to populate
% the "keywords" metadata in the PDF but will not be shown in the document
\sysmlkeywords{Machine Learning, SysML}

\vskip 0.3in

\begin{abstract}
This document provides a basic paper template and submission guidelines.
Abstracts must be a single paragraph, ideally between 4--6 sentences long.
Gross violations will trigger corrections at the camera-ready phase.
\end{abstract}
]

% this must go after the closing bracket ] following \twocolumn[ ...

% This command actually creates the footnote in the first column
% listing the affiliations and the copyright notice.
% The command takes one argument, which is text to display at the start of the footnote.
% The \sysmlEqualContribution command is standard text for equal contribution.
% Remove it (just {}) if you do not need this facility.

%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
\printAffiliationsAndNotice{\sysmlEqualContribution} % otherwise use the standard text.

\section{Electronic Submission}
\label{submission}

Submission to SysML 2019 will be entirely electronic, via a web site
(not email). Information about the submission process and \LaTeX\ templates
are available on the conference web site at:
\begin{center}
\textbf{\texttt{https://www.sysml.cc/}}
\end{center}

The guidelines below will be enforced for initial submissions and
camera-ready copies. Here is a brief summary:
\begin{itemize}
\item Submissions must be in PDF\@.
\item The maximum paper length is \textbf{10 pages excluding references.}
    (pages 11 and on must contain only references).
\item \textbf{Do not include author information or acknowledgements} in your
    initial submission.
\item Your paper should be in \textbf{10 point Times font}.
\item Make sure your PDF file only uses Type-1 fonts.
\item Place figure captions \emph{under} the figure (and omit titles from inside
    the graphic file itself). Place table captions \emph{over} the table.
\item References must include page numbers whenever possible and be as complete
    as possible. Place multiple citations in chronological order.
\item Do not alter the style template; in particular, do not compress the paper
    format by reducing the vertical spaces.
\item Keep your abstract brief and self-contained, one paragraph and roughly
    4--6 sentences. Gross violations will require correction at the
    camera-ready phase. The title should have content words capitalized.
\end{itemize}

\subsection{Submitting Papers}

\textbf{Paper Deadline:} The deadline for paper submission that is
advertised on the conference website is strict. If your full,
anonymized, submission does not reach us on time, it will not be
considered for publication. There is no separate abstract submission.

\textbf{Anonymous Submission:} SysML uses double-blind review: no identifying
author information may appear on the title page or in the paper
itself. Section~\ref{author info} gives further details.

\textbf{Simultaneous Submission:} SysML will not accept any paper which,
at the time of submission, is under review for another conference or
has already been published. This policy also applies to papers that
overlap substantially in technical content with conference papers
under review or previously published. SysML submissions must not be
submitted to other conferences during SysML's review period. Authors
may submit to SysML substantially different versions of journal papers
that are currently under review by the journal, but not yet accepted
at the time of submission. Informal publications, such as technical
reports or papers in workshop proceedings which do not appear in
print, do not fall under these restrictions.

\medskip

Authors must provide their manuscripts in \textbf{PDF} format.
Furthermore, please make sure that files contain only embedded Type-1 fonts
(e.g.,~using the program \texttt{pdffonts} in linux or using
File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
might come from graphics files imported into the document.

Authors using \textbf{Word} must convert their document to PDF\@. Most
of the latest versions of Word have the facility to do this
automatically. Submissions will not be accepted in Word format or any
format other than PDF\@. Really. We're not joking. Don't send Word.

Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
Those using \texttt{latex} and \texttt{dvips} may need the following
two commands:

{\footnotesize
\begin{verbatim}
dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
ps2pdf paper.ps
\end{verbatim}}
It is a zero following the ``-G'', which tells dvips to use
the config.pdf file. Newer \TeX\ distributions don't always need this
option.

Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
results. This program avoids the Type-3 font problem, and supports more
advanced features in the \texttt{microtype} package.

\textbf{Graphics files} should be a reasonable size, and included from
an appropriate format. Use vector formats (.eps/.pdf) for plots,
lossless bitmap formats (.png) for raster graphics with sharp lines, and
jpeg for photo-like images.

The style file uses the \texttt{hyperref} package to make clickable
links in documents. If this causes problems for you, add
\texttt{nohyperref} as one of the options to the \texttt{sysml2019}
usepackage statement.

\subsection{Submitting Final Camera-Ready Copy}

The final versions of papers accepted for publication should follow the
same format and naming convention as initial submissions, except that
author information (names and affiliations) should be given. See
Section~\ref{final author} for formatting instructions.

The footnote, ``Preliminary work. Under review by the SysML. Do not distribute.'' must be
modified to ``\textit{Proceedings of the
$\mathit{2}^{nd}$ SysML Conference},
Palo Alto, CA, USA, 2019.
Copyright 2019 by the author(s).''

For those using the \textbf{\LaTeX} style file, this change (and others) is
handled automatically by simply changing
$\mathtt{\backslash usepackage\{sysml2019\}}$ to
$$\mathtt{\backslash usepackage[accepted]\{sysml2019\}}$$
Authors using \textbf{Word} must edit the
footnote on the first page of the document themselves.

Camera-ready copies should have the title of the paper as running head
on each page except the first one. The running title consists of a
single line centered above a horizontal rule which is $1$~point thick.
The running head should be centered, bold and in $9$~point type. The
rule should be $10$~points above the main text. For those using the
\textbf{\LaTeX} style file, the original title is automatically set as running
head using the \texttt{fancyhdr} package which is included in the SysML
2019 style file package. In case that the original title exceeds the
size restrictions, a shorter form can be supplied by using

\verb|\sysmltitlerunning{...}|

just before $\mathtt{\backslash begin\{document\}}$.
Authors using \textbf{Word} must edit the header of the document themselves.

\section{Format of the Paper}

All submissions must follow the specified format.

\subsection{Length and Dimensions}

Papers must not exceed ten (10) pages, including all figures, tables,
and appendices, but excluding references.
Acknowledgements should be limited to grants and people who contributed to the paper.
Any submission that exceeds
this page limit, or that diverges significantly from the specified format,
will be rejected without review.

The text of the paper should be formatted in two columns, with an
overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
between the columns. The left margin should be 0.75~inches and the top
margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
whether you print on US letter or A4 paper, but all final versions
must be produced for US letter size.

The paper body should be set in 10~point type with a vertical spacing
of 11~points. Please use Times typeface throughout the text.

\subsection{Title}

The paper title should be set in 14~point bold type and centered
between two horizontal rules that are 1~point thick, with 1.0~inch
between the top rule and the top edge of the page. Capitalize the
first letter of content words and put the rest of the title in lower
case.

\subsection{Author Information for Submission}
\label{author info}

SysML uses double-blind review, so author information must not appear. If
you are using \LaTeX\/ and the \texttt{sysml2019.sty} file, use
\verb+\sysmlauthor{...}+ to specify authors and \verb+\sysmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
will not be printed unless \texttt{accepted} is passed as an argument to the
style file.
Submissions that include the author information will not
be reviewed.

\subsubsection{Self-Citations}

If you are citing published papers for which you are an author, refer
to yourself in the third person. In particular, do not use phrases
that reveal your identity (e.g., ``in previous work \cite{langley00}, we
have shown \ldots'').

Do not anonymize citations in the reference section. The only exception are manuscripts that are
not yet published (e.g., under submission). If you choose to refer to
such unpublished manuscripts \cite{anonymous}, anonymized copies have
to be submitted
as Supplementary Material via CMT\@. However, keep in mind that an SysML
paper should be self contained and should contain sufficient detail
for the reviewers to evaluate the work. In particular, reviewers are
not required to look at the Supplementary Material when writing their
review.

\subsubsection{Camera-Ready Author Information}
\label{final author}

If a paper is accepted, a final camera-ready copy must be prepared.
%
For camera-ready papers, author information should start 0.3~inches below the
bottom rule surrounding the title. The authors' names should appear in 10~point
bold type, in a row, separated by white space, and centered. Author names should
not be broken across lines. Unbolded superscripted numbers, starting 1, should
be used to refer to affiliations.

Affiliations should be numbered in the order of appearance. A single footnote
block of text should be used to list all the affiliations. (Academic
affiliations should list Department, University, City, State/Region, Country.
Similarly for industrial affiliations.)

Each distinct affiliations should be listed once. If an author has multiple
affiliations, multiple superscripts should be placed after the name, separated
by thin spaces. If the authors would like to highlight equal contribution by
multiple first authors, those authors should have an asterisk placed after their
name in superscript, and the term ``\textsuperscript{*}Equal contribution"
should be placed in the footnote block ahead of the list of affiliations. A
list of corresponding authors and their emails (in the format Full Name
\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
Ideally only one or two names should be listed.

A sample file with author names is included in the SysML2019 style file
package. Turn on the \texttt{[accepted]} option to the stylefile to
see the names rendered. All of the guidelines above are implemented
by the \LaTeX\ style file.

\subsection{Abstract}

The paper abstract should begin in the left column, 0.4~inches below the final
address. The heading `Abstract' should be centered, bold, and in 11~point type.
The abstract body should use 10~point type, with a vertical spacing of
11~points, and should be indented 0.25~inches more than normal on left-hand and
right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
sentences. Gross violations will require correction at the camera-ready phase.

\subsection{Partitioning the Text}

You should organize your paper into sections and paragraphs to help
readers place a structure on the material and understand its
contributions.

\subsubsection{Sections and Subsections}

Section headings should be numbered, flush left, and set in 11~pt bold
type with the content words capitalized. Leave 0.25~inches of space
before the heading and 0.15~inches after the heading.

Similarly, subsection headings should be numbered, flush left, and set
in 10~pt bold type with the content words capitalized. Leave
0.2~inches of space before the heading and 0.13~inches afterward.

Finally, subsubsection headings should be numbered, flush left, and
set in 10~pt small caps with the content words capitalized. Leave
0.18~inches of space before the heading and 0.1~inches after the
heading.

Please use no more than three levels of headings.

\subsubsection{Paragraphs and Footnotes}

Within each section or subsection, you should further partition the
paper into paragraphs. Do not indent the first line of a given
paragraph, but insert a blank line between succeeding ones.

You can use footnotes\footnote{Footnotes
should be complete sentences.} to provide readers with additional
information about a topic without interrupting the flow of the paper.
Indicate footnotes with a number in the text where the point is most
relevant. Place the footnote in 9~point type at the bottom of the
column in which it appears. Precede the first footnote in a column
with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
appear in each column, in the same order as they appear in the text,
but spread them across columns and pages if possible.}

\subsection{Figures}

You may want to include figures in the paper to illustrate
your approach and results. Such artwork should be centered,
legible, and separated from the text. Lines should be dark and at
least 0.5~points thick for purposes of reproduction, and text should
not appear on a gray background.

Label all distinct components of each figure. If the figure takes the
form of a graph, then give a name for each axis and include a legend
that briefly describes each curve. Do not include a title inside the
figure; instead, the caption should serve this function.

Number figures sequentially, placing the figure number and caption
\emph{after} the graphics, with at least 0.1~inches of space before
the caption and 0.1~inches after it. The figure caption should be set in
9~point type and centered unless it runs two or more lines, in which
case it should be flush left. You may float figures to the top or
bottom of a column, and you may set wide figures across both columns
(use the environment \texttt{figure*} in \LaTeX). Always place
two-column figures at the top or bottom of the page.

\subsection{Algorithms}

If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
environments to format pseudocode. These require
the corresponding stylefiles, algorithm.sty and
algorithmic.sty, which are supplied with this package.
Algorithm~\ref{alg:example} shows an example.

\begin{algorithm}[tb]
   \caption{Bubble Sort}
   \label{alg:example}
\begin{algorithmic}
   \STATE {\bfseries Input:} data $x_i$, size $m$
   \REPEAT
   \STATE Initialize $noChange = true$.
   \FOR{$i=1$ {\bfseries to} $m-1$}
   \IF{$x_i > x_{i+1}$}
   \STATE Swap $x_i$ and $x_{i+1}$
   \STATE $noChange = false$
   \ENDIF
   \ENDFOR
   \UNTIL{$noChange$ is $true$}
\end{algorithmic}
\end{algorithm}

\subsection{Tables}

You may also want to include tables that summarize material. Like
figures, these should be centered, legible, and numbered consecutively.
However, place the title \emph{above} the table with at least
0.1~inches of space before the title and the same after it, as in
Table~\ref{sample-table}. The table title should be set in 9~point
type and centered unless it runs two or more lines, in which case it
should be flush left.

% Note use of \abovespace and \belowspace to get reasonable spacing
% above and below tabular lines.

\begin{table}[t]
\caption{Classification accuracies for naive Bayes and flexible
Bayes on various data sets.}
\label{sample-table}
\vskip 0.15in
\begin{center}
\begin{small}
\begin{sc}
\begin{tabular}{lcccr}
\toprule
Data set & Naive & Flexible & Better? \\
\midrule
Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
\bottomrule
\end{tabular}
\end{sc}
\end{small}
\end{center}
\vskip -0.1in
\end{table}

Tables contain textual material, whereas figures contain graphical material.
Specify the contents of each row and column in the table's topmost
row. Again, you may float tables to a column's top or bottom, and set
wide tables across both columns. Place two-column tables at the
top or bottom of the page.

\subsection{Citations and References}

Please use APA reference format regardless of your formatter
or word processor. If you rely on the \LaTeX\/ bibliographic
facility, use \texttt{natbib.sty} and \texttt{sysml2019.bst}
included in the style-file package to obtain this format.

Citations within the text should include the authors' last names and
year. If the authors' names are included in the sentence, place only
the year in parentheses, for example when referencing Arthur Samuel's
pioneering work \yrcite{Samuel59}. Otherwise place the entire
reference in parentheses with the authors and year separated by a
comma \cite{Samuel59}. List multiple references separated by
semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
construct only for citations with three or more authors or after
listing all authors to a publication in an earlier reference \cite{MachineLearningI}.

Authors should cite their own work in the third person
in the initial version of their paper submitted for blind review.
Please refer to Section~\ref{author info} for detailed instructions on how to
cite your own papers.

Use an unnumbered first-level section heading for the references, and use a
hanging indent style, with the first line of the reference flush against the
left margin and subsequent lines indented by 10 points. The references at the
end of this document give examples for journal articles \cite{Samuel59},
conference publications \cite{langley00}, book chapters \cite{Newell81}, books
\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
\cite{mitchell80}, and dissertations \cite{kearns89}.

Alphabetize references by the surnames of the first authors, with
single author entries preceding multiple author entries. Order
references for the same authors by year of publication, with the
earliest first. Make sure that each reference includes all relevant
information (e.g., page numbers).

Please put some effort into making references complete, presentable, and
consistent. If using bibtex, please protect capital letters of names and
abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
in your .bib file.

\subsection{Software and Data}

We strongly encourage the publication of software and data with the
camera-ready version of the paper whenever appropriate. This can be
done by including a URL in the camera-ready copy. However, do not
include URLs that reveal your institution or identity in your
submission for review. Instead, provide an anonymous URL or upload
the material as ``Supplementary Material'' into the CMT reviewing
system. Note that reviewers are not required to look at this material
when writing their review.

% Acknowledgements should only appear in the accepted version.
\section*{Acknowledgements}

\textbf{Do not} include acknowledgements in the initial version of
the paper submitted for blind review.

If a paper is accepted, the final camera-ready version can (and
probably should) include acknowledgements. In this case, please
place such acknowledgements in an unnumbered section at the
end of the paper. Typically, this will include thanks to reviewers
who gave useful comments, to colleagues who contributed to the ideas,
and to funding agencies and corporate sponsors that provided financial
support.

% In the unusual situation where you want a paper to appear in the
% references without citing it in the main text, use \nocite
\nocite{langley00}

\bibliography{paper}
\bibliographystyle{sysml2019}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix
\section{Do \emph{not} have an appendix here}

\textbf{\emph{Do not put content after the references.}}
%
Put anything that you might normally include after the references in a separate
supplementary file.

We recommend that you build supplementary material in a separate document.
If you must create one PDF and cut it up, please be careful to use a tool that
doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
pdftk usually works fine.

\textbf{Please do not use Apple's preview to cut off supplementary material.} In
previous years it has altered margins, and created headaches at the camera-ready
stage.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

% This document was modified from the file originally made available by
% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
% by Iain Murray in 2018. It was modified from a version from Dan Roy in
% 2017, which was based on a version from Lise Getoor and Tobias
% Scheffer, which was slightly modified from the 2010 version by
% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
% slightly modified from Prasad Tadepalli's 2007 version which is a
% lightly changed version of the previous year's version by Andrew
% Moore, which was in turn edited from those of Kristian Kersting and
% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2018-09-26 paper.tex
ToC stub

@@
 \usepackage{hyperref}
-
-% Attempt to make hyperref and algorithmic work together better:
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
 
@@
 % Therefore, a short form for the running title is supplied here:
-\sysmltitlerunning{Submission and Formatting Instructions for SysML 2019}
+%\sysmltitlerunning{Guild AI: NEEDS A TITLE}
 
@@
 \twocolumn[
-\sysmltitle{Submission and Formatting Instructions for SysML 2019}
-
-% It is OKAY to include author information, even for blind
-% submissions: the style file will automatically remove it for you
-% unless you've provided the [accepted] option to the sysml2019
-% package.
+\sysmltitle{Guild AI: Package management for machine learning models}
 
@@
 
-% You can specify symbols, otherwise they are numbered in order.
-% Ideally, you should not use this facility. Affiliations will be numbered
-% in order of appearance and this is the preferred way.
-\sysmlsetsymbol{equal}{*}
-
 \begin{sysmlauthorlist}
-\sysmlauthor{Aeiau Zzzz}{equal,to}
-\sysmlauthor{Bauiu C.~Yyyy}{equal,to,goo}
-\sysmlauthor{Cieua Vvvvv}{goo}
-\sysmlauthor{Iaesut Saoeu}{ed}
-\sysmlauthor{Fiuea Rrrr}{to}
-\sysmlauthor{Tateu H.~Yasehe}{ed,to,goo}
-\sysmlauthor{Aaoeu Iasoh}{goo}
-\sysmlauthor{Buiui Eueu}{ed}
-\sysmlauthor{Aeuia Zzzz}{ed}
-\sysmlauthor{Bieea C.~Yyyy}{to,goo}
-\sysmlauthor{Teoau Xxxx}{ed}
-\sysmlauthor{Eee Pppp}{ed}
+\sysmlauthor{Garrett Smith}{guild}
 \end{sysmlauthorlist}
 
-\sysmlaffiliation{to}{Department of Computation, University of Torontoland, Torontoland, Canada}
-\sysmlaffiliation{goo}{Googol ShallowMind, New London, Michigan, USA}
-\sysmlaffiliation{ed}{School of Computation, University of Edenborrow, Edenborrow, United Kingdom}
+\sysmlaffiliation{guild}{Guild AI, Chicago, Illinois, USA}
 
-\sysmlcorrespondingauthor{Cieua Vvvvv}{c.vvvvv@googol.com}
-\sysmlcorrespondingauthor{Eee Pppp}{ep@eden.co.uk}
+\sysmlcorrespondingauthor{Garrett Smith}{garrett@guild.ai}
 
@@
 % the "keywords" metadata in the PDF but will not be shown in the document
-\sysmlkeywords{Machine Learning, SysML}
+\sysmlkeywords{Guild AI, SysML}
 
@@
 \begin{abstract}
-This document provides a basic paper template and submission guidelines.
-Abstracts must be a single paragraph, ideally between 4--6 sentences long.
-Gross violations will trigger corrections at the camera-ready phase.
+
+  We present Guild AI, an open source toolkit that facilitates model
+  reuse for application development by applying traditional software
+  packaging constructs to the domain of machine learning. Package
+  management strategies are central to successful software
+  ecosystems. Examples include \href{https://www.npmjs.com/}{npm} for
+  JavaScript, \href{https://wiki.debian.org/Apt}{APT} for Debian, and
+  \href{https://pip.pypa.io}{pip} for Python. While such tools excel
+  at creating traditional software packages, machine learning
+  applications present unique requirements that call for
+  specialization. Guild AI combines the proven effectiveness of
+  package managers with novel features to enable machine learning
+  model reuse for application development across a variety of use
+  cases.
+
 \end{abstract}
@@
 
-%\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
-\printAffiliationsAndNotice{\sysmlEqualContribution} % otherwise use the standard text.
+\printAffiliationsAndNotice{}  % leave blank if no need to mention equal contribution
+%\printAffiliationsAndNotice{\sysmlEqualContribution} % otherwise use the standard text.
 
-\section{Electronic Submission}
-\label{submission}
+\section{Introduction}
 
-Submission to SysML 2019 will be entirely electronic, via a web site
-(not email). Information about the submission process and \LaTeX\ templates
-are available on the conference web site at:
-\begin{center}
-\textbf{\texttt{https://www.sysml.cc/}}
-\end{center}
+TODO:
 
-The guidelines below will be enforced for initial submissions and
-camera-ready copies. Here is a brief summary:
-\begin{itemize}
-\item Submissions must be in PDF\@.
-\item The maximum paper length is \textbf{10 pages excluding references.}
-    (pages 11 and on must contain only references).
-\item \textbf{Do not include author information or acknowledgements} in your
-    initial submission.
-\item Your paper should be in \textbf{10 point Times font}.
-\item Make sure your PDF file only uses Type-1 fonts.
-\item Place figure captions \emph{under} the figure (and omit titles from inside
-    the graphic file itself). Place table captions \emph{over} the table.
-\item References must include page numbers whenever possible and be as complete
-    as possible. Place multiple citations in chronological order.
-\item Do not alter the style template; in particular, do not compress the paper
-    format by reducing the vertical spaces.
-\item Keep your abstract brief and self-contained, one paragraph and roughly
-    4--6 sentences. Gross violations will require correction at the
-    camera-ready phase. The title should have content words capitalized.
-\end{itemize}
+- What problem is being solved?
 
-\subsection{Submitting Papers}
+- How package managers facilitate code reuse
 
-\textbf{Paper Deadline:} The deadline for paper submission that is
-advertised on the conference website is strict. If your full,
-anonymized, submission does not reach us on time, it will not be
-considered for publication. There is no separate abstract submission.
+\subsection{Related Work}
 
-\textbf{Anonymous Submission:} SysML uses double-blind review: no identifying
-author information may appear on the title page or in the paper
-itself. Section~\ref{author info} gives further details.
+- How machine learning models are distributed today (pip, GitHub
+projects)
 
-\textbf{Simultaneous Submission:} SysML will not accept any paper which,
-at the time of submission, is under review for another conference or
-has already been published. This policy also applies to papers that
-overlap substantially in technical content with conference papers
-under review or previously published. SysML submissions must not be
-submitted to other conferences during SysML's review period. Authors
-may submit to SysML substantially different versions of journal papers
-that are currently under review by the journal, but not yet accepted
-at the time of submission. Informal publications, such as technical
-reports or papers in workshop proceedings which do not appear in
-print, do not fall under these restrictions.
+- Frameworks and libraries
 
-\medskip
+- TensorFlow Hub
 
-Authors must provide their manuscripts in \textbf{PDF} format.
-Furthermore, please make sure that files contain only embedded Type-1 fonts
-(e.g.,~using the program \texttt{pdffonts} in linux or using
-File/DocumentProperties/Fonts in Acrobat). Other fonts (like Type-3)
-might come from graphics files imported into the document.
+- Keras Applications
 
-Authors using \textbf{Word} must convert their document to PDF\@. Most
-of the latest versions of Word have the facility to do this
-automatically. Submissions will not be accepted in Word format or any
-format other than PDF\@. Really. We're not joking. Don't send Word.
+- ???
 
-Those who use \textbf{\LaTeX} should avoid including Type-3 fonts.
-Those using \texttt{latex} and \texttt{dvips} may need the following
-two commands:
+\subsection{Differences}
+
+- How is Guild different from these cited projects?
+
+- Include model and operation definitions
+
+- Reuse through distribution and patching
+
+- Federation (protocol driven, intelligence moved to the perimeter).
+
+\section{Concepts}
+
+\subsection{Projects}
+
+\subsection{Packages}
+
+\subsection{Models}
+
+\subsection{Operations}
+
+\subsection{Flags}
+
+\subsection{Resources}
+
+\subsection{Runs}
+
+\subsection{Environments}
+
+\subsection{Workflows}
+
+\section{Use Cases}
+
+\subsection{Publish a Model for Reuse}
+
+\subsection{Use a Published Model}
+
+\subsection{Package Third Party Models}
+
+\subsection{Team Collaboration}
+
+\subsection{Streamline Model Developer Workflow}
+
+\subsection{Manage Run Artifacts}
+
+\section{Using Models}
+
+\subsection{Packaged Models}
+
+\subsection{Project Models}
+
+\subsection{Listing Available Models and Operations}
+
+\subsection{Getting Help for Models}
+
+\subsection{Running Operations}
+
+\subsection{Viewing and Comparing Runs}
+
+\subsection{Exporting Model Artifacts}
+
+\section{Managing Runs}
+
+- What is a run (from an operation)
+
+- What is a run concretely (i.e. directory, etc.)
+
+\subsection{Starging a Run}
+
+\subsection{Listing Runs}
+
+\subsection{Getting Run Information}
+
+\subsection{Deleting Runs}
+
+\subsection{Archiving and Restoring Runs}
+
+\subsection{Run Dependencies}
+
+\subsection{Remote Runs}
+
+\section{Developing Reusable Models}
+
+\subsection{Developing a Model from Scratch}
+
+- How to choose a model boundary?
+
+- How to define operations
+
+\subsection{Customizing Models}
+
+\subsubsection{Model Inheritance}
+
+\subsubsection{Configuration Mixins}
+
+\subsubsection{Modifying Operations}
+
+\subsubsection{Modifying Flag Values}
+
+\subsubsection{Reusing Python Main Modules}
+
+\subsection{Packaging}
+
+\subsection{Patching Strategies}
+
+\section{Implementation}
+
+- Core - written in Python, etc.
+
+\subsection{Command Line Interface}
+
+\subsection{Configuration Processing}
+
+\subsection{Requires Resource Resolution}
+
+\subsection{Packaging}
+
+\subsection{Run Indexing}
+
+\subsection{Run Visualization}
+
+\subsection{Remote Environments}
+
+\section{Status}
+
+- Apache 2.0
+
+\subsection{History and Lessons Learned}
+
+\subsection{Packages}
+
+\subsection{Early Use}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\section{Typography}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% Delete this to end of doc
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Verbatim}
 
@@
 ps2pdf paper.ps
+another line yo
 \end{verbatim}}
-It is a zero following the ``-G'', which tells dvips to use
-the config.pdf file. Newer \TeX\ distributions don't always need this
-option.
 
-Using \texttt{pdflatex} rather than \texttt{latex}, often gives better
-results. This program avoids the Type-3 font problem, and supports more
-advanced features in the \texttt{microtype} package.
+You can copy the file by running \verb|cp foo bar| where \textit{foo}
+is some file you want to copy and \textit{bar} is something else.
 
-\textbf{Graphics files} should be a reasonable size, and included from
-an appropriate format. Use vector formats (.eps/.pdf) for plots,
-lossless bitmap formats (.png) for raster graphics with sharp lines, and
-jpeg for photo-like images.
+\subsection{Italics}
 
-The style file uses the \texttt{hyperref} package to make clickable
-links in documents. If this causes problems for you, add
-\texttt{nohyperref} as one of the options to the \texttt{sysml2019}
-usepackage statement.
+\textit{Proceedings of the $\mathit{2}^{nd}$ SysML Conference}
 
-\subsection{Submitting Final Camera-Ready Copy}
+And \emph{this is for emphasis!}
 
-The final versions of papers accepted for publication should follow the
-same format and naming convention as initial submissions, except that
-author information (names and affiliations) should be given. See
-Section~\ref{final author} for formatting instructions.
+\subsection{Bold}
 
-The footnote, ``Preliminary work. Under review by the SysML. Do not distribute.'' must be
-modified to ``\textit{Proceedings of the
-$\mathit{2}^{nd}$ SysML Conference},
-Palo Alto, CA, USA, 2019.
-Copyright 2019 by the author(s).''
+I will \textbf{make this bold} yo.
 
-For those using the \textbf{\LaTeX} style file, this change (and others) is
-handled automatically by simply changing
-$\mathtt{\backslash usepackage\{sysml2019\}}$ to
-$$\mathtt{\backslash usepackage[accepted]\{sysml2019\}}$$
-Authors using \textbf{Word} must edit the
-footnote on the first page of the document themselves.
+\subsection{Teletype}
 
-Camera-ready copies should have the title of the paper as running head
-on each page except the first one. The running title consists of a
-single line centered above a horizontal rule which is $1$~point thick.
-The running head should be centered, bold and in $9$~point type. The
-rule should be $10$~points above the main text. For those using the
-\textbf{\LaTeX} style file, the original title is automatically set as running
-head using the \texttt{fancyhdr} package which is included in the SysML
-2019 style file package. In case that the original title exceeds the
-size restrictions, a shorter form can be supplied by using
+Set the value to \texttt{accepted} and everything will be okay.
 
-\verb|\sysmltitlerunning{...}|
+\subsection{Dots}
 
-just before $\mathtt{\backslash begin\{document\}}$.
-Authors using \textbf{Word} must edit the header of the document themselves.
+ldots: \ldots
 
-\section{Format of the Paper}
+dots: \dots
 
-All submissions must follow the specified format.
+\subsection{Less than, greater than}
 
-\subsection{Length and Dimensions}
+\textless{}email@domain.com\textgreater{}
 
-Papers must not exceed ten (10) pages, including all figures, tables,
-and appendices, but excluding references.
-Acknowledgements should be limited to grants and people who contributed to the paper.
-Any submission that exceeds
-this page limit, or that diverges significantly from the specified format,
-will be rejected without review.
+\subsection{Footnotes}
 
-The text of the paper should be formatted in two columns, with an
-overall width of 6.75~inches, height of 9.0~inches, and 0.25~inches
-between the columns. The left margin should be 0.75~inches and the top
-margin 1.0~inch (2.54~cm). The right and bottom margins will depend on
-whether you print on US letter or A4 paper, but all final versions
-must be produced for US letter size.
-
-The paper body should be set in 10~point type with a vertical spacing
-of 11~points. Please use Times typeface throughout the text.
-
-\subsection{Title}
-
-The paper title should be set in 14~point bold type and centered
-between two horizontal rules that are 1~point thick, with 1.0~inch
-between the top rule and the top edge of the page. Capitalize the
-first letter of content words and put the rest of the title in lower
-case.
-
-\subsection{Author Information for Submission}
-\label{author info}
-
-SysML uses double-blind review, so author information must not appear. If
-you are using \LaTeX\/ and the \texttt{sysml2019.sty} file, use
-\verb+\sysmlauthor{...}+ to specify authors and \verb+\sysmlaffiliation{...}+ to specify affiliations. (Read the TeX code used to produce this document for an example usage.) The author information
-will not be printed unless \texttt{accepted} is passed as an argument to the
-style file.
-Submissions that include the author information will not
-be reviewed.
-
-\subsubsection{Self-Citations}
-
-If you are citing published papers for which you are an author, refer
-to yourself in the third person. In particular, do not use phrases
-that reveal your identity (e.g., ``in previous work \cite{langley00}, we
-have shown \ldots'').
-
-Do not anonymize citations in the reference section. The only exception are manuscripts that are
-not yet published (e.g., under submission). If you choose to refer to
-such unpublished manuscripts \cite{anonymous}, anonymized copies have
-to be submitted
-as Supplementary Material via CMT\@. However, keep in mind that an SysML
-paper should be self contained and should contain sufficient detail
-for the reviewers to evaluate the work. In particular, reviewers are
-not required to look at the Supplementary Material when writing their
-review.
-
-\subsubsection{Camera-Ready Author Information}
-\label{final author}
-
-If a paper is accepted, a final camera-ready copy must be prepared.
-%
-For camera-ready papers, author information should start 0.3~inches below the
-bottom rule surrounding the title. The authors' names should appear in 10~point
-bold type, in a row, separated by white space, and centered. Author names should
-not be broken across lines. Unbolded superscripted numbers, starting 1, should
-be used to refer to affiliations.
-
-Affiliations should be numbered in the order of appearance. A single footnote
-block of text should be used to list all the affiliations. (Academic
-affiliations should list Department, University, City, State/Region, Country.
-Similarly for industrial affiliations.)
-
-Each distinct affiliations should be listed once. If an author has multiple
-affiliations, multiple superscripts should be placed after the name, separated
-by thin spaces. If the authors would like to highlight equal contribution by
-multiple first authors, those authors should have an asterisk placed after their
-name in superscript, and the term ``\textsuperscript{*}Equal contribution"
-should be placed in the footnote block ahead of the list of affiliations. A
-list of corresponding authors and their emails (in the format Full Name
-\textless{}email@domain.com\textgreater{}) can follow the list of affiliations.
-Ideally only one or two names should be listed.
-
-A sample file with author names is included in the SysML2019 style file
-package. Turn on the \texttt{[accepted]} option to the stylefile to
-see the names rendered. All of the guidelines above are implemented
-by the \LaTeX\ style file.
-
-\subsection{Abstract}
-
-The paper abstract should begin in the left column, 0.4~inches below the final
-address. The heading `Abstract' should be centered, bold, and in 11~point type.
-The abstract body should use 10~point type, with a vertical spacing of
-11~points, and should be indented 0.25~inches more than normal on left-hand and
-right-hand margins. Insert 0.4~inches of blank space after the body. Keep your
-abstract brief and self-contained, limiting it to one paragraph and roughly 4--6
-sentences. Gross violations will require correction at the camera-ready phase.
-
-\subsection{Partitioning the Text}
-
-You should organize your paper into sections and paragraphs to help
-readers place a structure on the material and understand its
-contributions.
-
-\subsubsection{Sections and Subsections}
-
-Section headings should be numbered, flush left, and set in 11~pt bold
-type with the content words capitalized. Leave 0.25~inches of space
-before the heading and 0.15~inches after the heading.
-
-Similarly, subsection headings should be numbered, flush left, and set
-in 10~pt bold type with the content words capitalized. Leave
-0.2~inches of space before the heading and 0.13~inches afterward.
-
-Finally, subsubsection headings should be numbered, flush left, and
-set in 10~pt small caps with the content words capitalized. Leave
-0.18~inches of space before the heading and 0.1~inches after the
-heading.
-
-Please use no more than three levels of headings.
-
-\subsubsection{Paragraphs and Footnotes}
-
-Within each section or subsection, you should further partition the
-paper into paragraphs. Do not indent the first line of a given
-paragraph, but insert a blank line between succeeding ones.
-
-You can use footnotes\footnote{Footnotes
-should be complete sentences.} to provide readers with additional
-information about a topic without interrupting the flow of the paper.
-Indicate footnotes with a number in the text where the point is most
-relevant. Place the footnote in 9~point type at the bottom of the
-column in which it appears. Precede the first footnote in a column
-with a horizontal rule of 0.8~inches.\footnote{Multiple footnotes can
-appear in each column, in the same order as they appear in the text,
-but spread them across columns and pages if possible.}
-
-\subsection{Figures}
-
-You may want to include figures in the paper to illustrate
-your approach and results. Such artwork should be centered,
-legible, and separated from the text. Lines should be dark and at
-least 0.5~points thick for purposes of reproduction, and text should
-not appear on a gray background.
-
-Label all distinct components of each figure. If the figure takes the
-form of a graph, then give a name for each axis and include a legend
-that briefly describes each curve. Do not include a title inside the
-figure; instead, the caption should serve this function.
-
-Number figures sequentially, placing the figure number and caption
-\emph{after} the graphics, with at least 0.1~inches of space before
-the caption and 0.1~inches after it. The figure caption should be set in
-9~point type and centered unless it runs two or more lines, in which
-case it should be flush left. You may float figures to the top or
-bottom of a column, and you may set wide figures across both columns
-(use the environment \texttt{figure*} in \LaTeX). Always place
-two-column figures at the top or bottom of the page.
-
-\subsection{Algorithms}
-
-If you are using \LaTeX, please use the ``algorithm'' and ``algorithmic''
-environments to format pseudocode. These require
-the corresponding stylefiles, algorithm.sty and
-algorithmic.sty, which are supplied with this package.
-Algorithm~\ref{alg:example} shows an example.
-
-\begin{algorithm}[tb]
-   \caption{Bubble Sort}
-   \label{alg:example}
-\begin{algorithmic}
-   \STATE {\bfseries Input:} data $x_i$, size $m$
-   \REPEAT
-   \STATE Initialize $noChange = true$.
-   \FOR{$i=1$ {\bfseries to} $m-1$}
-   \IF{$x_i > x_{i+1}$}
-   \STATE Swap $x_i$ and $x_{i+1}$
-   \STATE $noChange = false$
-   \ENDIF
-   \ENDFOR
-   \UNTIL{$noChange$ is $true$}
-\end{algorithmic}
-\end{algorithm}
+You can use footnotes\footnote{Footnotes should be complete
+  sentences.} which will be super awesome. Don't ask me how it works.
 
 \subsection{Tables}
-
-You may also want to include tables that summarize material. Like
-figures, these should be centered, legible, and numbered consecutively.
-However, place the title \emph{above} the table with at least
-0.1~inches of space before the title and the same after it, as in
-Table~\ref{sample-table}. The table title should be set in 9~point
-type and centered unless it runs two or more lines, in which case it
-should be flush left.
-
-% Note use of \abovespace and \belowspace to get reasonable spacing
-% above and below tabular lines.
 
@@
 \label{sample-table}
-\vskip 0.15in
 \begin{center}
@@
 
-Tables contain textual material, whereas figures contain graphical material.
-Specify the contents of each row and column in the table's topmost
-row. Again, you may float tables to a column's top or bottom, and set
-wide tables across both columns. Place two-column tables at the
-top or bottom of the page.
+\subsection{Citations}
 
-\subsection{Citations and References}
-
-Please use APA reference format regardless of your formatter
-or word processor. If you rely on the \LaTeX\/ bibliographic
-facility, use \texttt{natbib.sty} and \texttt{sysml2019.bst}
-included in the style-file package to obtain this format.
-
-Citations within the text should include the authors' last names and
-year. If the authors' names are included in the sentence, place only
-the year in parentheses, for example when referencing Arthur Samuel's
-pioneering work \yrcite{Samuel59}. Otherwise place the entire
-reference in parentheses with the authors and year separated by a
-comma \cite{Samuel59}. List multiple references separated by
-semicolons \cite{kearns89,Samuel59,mitchell80}. Use the `et~al.'
-construct only for citations with three or more authors or after
-listing all authors to a publication in an earlier reference \cite{MachineLearningI}.
-
-Authors should cite their own work in the third person
-in the initial version of their paper submitted for blind review.
-Please refer to Section~\ref{author info} for detailed instructions on how to
-cite your own papers.
-
-Use an unnumbered first-level section heading for the references, and use a
-hanging indent style, with the first line of the reference flush against the
-left margin and subsequent lines indented by 10 points. The references at the
-end of this document give examples for journal articles \cite{Samuel59},
-conference publications \cite{langley00}, book chapters \cite{Newell81}, books
-\cite{DudaHart2nd}, edited volumes \cite{MachineLearningI}, technical reports
-\cite{mitchell80}, and dissertations \cite{kearns89}.
-
-Alphabetize references by the surnames of the first authors, with
-single author entries preceding multiple author entries. Order
-references for the same authors by year of publication, with the
-earliest first. Make sure that each reference includes all relevant
-information (e.g., page numbers).
-
-Please put some effort into making references complete, presentable, and
-consistent. If using bibtex, please protect capital letters of names and
-abbreviations in titles, for example, use \{B\}ayesian or \{L\}ipschitz
-in your .bib file.
-
-\subsection{Software and Data}
-
-We strongly encourage the publication of software and data with the
-camera-ready version of the paper whenever appropriate. This can be
-done by including a URL in the camera-ready copy. However, do not
-include URLs that reveal your institution or identity in your
-submission for review. Instead, provide an anonymous URL or upload
-the material as ``Supplementary Material'' into the CMT reviewing
-system. Note that reviewers are not required to look at this material
-when writing their review.
-
-% Acknowledgements should only appear in the accepted version.
-\section*{Acknowledgements}
-
-\textbf{Do not} include acknowledgements in the initial version of
-the paper submitted for blind review.
-
-If a paper is accepted, the final camera-ready version can (and
-probably should) include acknowledgements. In this case, please
-place such acknowledgements in an unnumbered section at the
-end of the paper. Typically, this will include thanks to reviewers
-who gave useful comments, to colleagues who contributed to the ideas,
-and to funding agencies and corporate sponsors that provided financial
-support.
-
-% In the unusual situation where you want a paper to appear in the
-% references without citing it in the main text, use \nocite
-\nocite{langley00}
+I really like TensorFlow \cite{tensorflow2015-whitepaper}.
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% DELETE THIS PART. DO NOT PLACE CONTENT AFTER THE REFERENCES!
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\appendix
-\section{Do \emph{not} have an appendix here}
-
-\textbf{\emph{Do not put content after the references.}}
-%
-Put anything that you might normally include after the references in a separate
-supplementary file.
-
-We recommend that you build supplementary material in a separate document.
-If you must create one PDF and cut it up, please be careful to use a tool that
-doesn't alter the margins, and that doesn't aggressively rewrite the PDF file.
-pdftk usually works fine.
-
-\textbf{Please do not use Apple's preview to cut off supplementary material.} In
-previous years it has altered margins, and created headaches at the camera-ready
-stage.
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}
-
-% This document was modified from the file originally made available by
-% Pat Langley and Andrea Danyluk for ICML-2K. This version was created
-% by Iain Murray in 2018. It was modified from a version from Dan Roy in
-% 2017, which was based on a version from Lise Getoor and Tobias
-% Scheffer, which was slightly modified from the 2010 version by
-% Thorsten Joachims & Johannes Fuernkranz, slightly modified from the
-% 2009 version by Kiri Wagstaff and Sam Roweis's 2008 version, which is
-% slightly modified from Prasad Tadepalli's 2007 version which is a
-% lightly changed version of the previous year's version by Andrew
-% Moore, which was in turn edited from those of Kristian Kersting and
-% Codrina Lauth. Alex Smola contributed to the algorithmic style files.

### 2018-09-27 paper.tex
Wip

@@
   JavaScript, \href{https://wiki.debian.org/Apt}{APT} for Debian, and
-  \href{https://pip.pypa.io}{pip} for Python. While such tools excel
-  at creating traditional software packages, machine learning
-  applications present unique requirements that call for
+  \href{https://pip.pypa.io}{pip} for Python. Such tools excel at
+  creating traditional software packages. However, machine learning
+  applications present unique requirements that call for tool
   specialization. Guild AI combines the proven effectiveness of
@@
 
+Code reuse is a central tenet in software development and is supported
+by myriad techniques, abstractions, and tools. Effective code reuse
+allows developers to leverage prior work in a consistent, reliable
+manner that saves time and improves software quality. In this paper we
+consider code reuse in terms of \emph{packaged software} in the
+context of machine learning.
+
+\subsection{Traditional packaged software}
+
+Packaged software is software that is organized in a way that can be
+easily installed and used by \emph{users}. A user is a consumer of
+software, rather than a producer or developer. A user may be software
+developer, in the case of consuming software libraries or frameworks,
+or she may be an end-user who uses software as a program using a
+graphical or command line interface. In both cases, packaged software
+may be provided in units that the user can install and start using
+quickly and reliably.
+
+This is an example of installing packaged software:
+
+{\footnotesize
+\begin{verbatim}
+ $ pip install tensorflow
+\end{verbatim}}
+
+By running this command, a user is using a \emph{package manager}---in
+this case the program \verb|pip|---to install a package named
+\verb|tensorflow|. With this innocuous command, the user implicitly expects
+a number of things:
+
+\begin{itemize}
+\item The Python module \verb|tensorflow| should be installed
+\item Additional Python modules required by \verb|tensorflow| should
+  also be installed
+\item Installed software should work as expected on the target system
+\item At a future date \verb|tensorflow| may be similarly uninstalled along
+  with its no-longer-needed required packages
+\item The act of installing and uninstalling \verb|tensorflow| should
+  not break or otherwise destabilize other installed software on the
+  target system
+\end{itemize}
+
+Such a package management facilities are essential to code reuse at
+the system level. Package managers allow users to consume and manage
+complex software systems with simple commands in a way that maintains
+the integrity of other installed software. They support rapid
+experimentation with new software as users are free to install, use,
+and evaluate packages with the confidence that they can safely remove
+that software later.
+
+Package managers promote healthy software ecosystems by facilitating
+software \emph{publishing}. Software authors use packaging tools to
+create the installable software units---\emph{packages}---that are so
+easily consumed by users. By publishing packaged software, developers
+signify that their software will work as advertised if installed using
+the supported tools.
+
+Immense software ecosystems that are enabled by package managers
+include Python, JavaScript, Ruby, Go, and R. The GNU/Linux operating
+system itself is an ecosystem of package management ecosystems
+including packaging schemes from Debian, RedHat, Gentoo, and Arch
+distributions. Package managers are established cornerstones of
+software reuse across languages and operating systems.
+
+\subsection{Code reuse and machine learning models}
+
+A \emph{machine learning model} is challenging to define as models
+have different contexts. In the most general context, models are
+mathematical concepts or language that represents a system
+(needref). In the context of machine learning, models may be
+represented by computer source code, either explicitly as declared
+structures, or implicitly by way of executable instructions that
+perform model related tasks. A \emph{trained model} is a model that
+has learned some representation of a system through the process of
+computer based optimization.
+
+For the purpose of our discussion, a machine learning model is a
+software representation of a specific mathetical concept that can be
+trained by a computer. Models may be in various states:
+\emph{uninitialized}, \emph{initialized}, \emph{partially trained},
+\emph{fully trained}. Regardless of state, the distinguishing feature
+of machine learning models for our purpose is that they support
+runnable computer operations.
+
+Models---and in particular \emph{trained models}--- are similar to
+traditional software in that they can be executed to perform
+computations. In fact, the purpose of training a model is to create a
+computer program. The difference between a trained model and a human
+authored program is one of method: a trained model is learned by an
+algorithm while a human authored program is written manually.
+
 TODO:
@@
 
+Need to define reuse. Start with traditional softwar reuse and make it
+clear that Guild addresses model reuse. What is model reuse?
+
 - How package managers facilitate code reuse
+
+Apply analogy of system packaging and the importance of formalizing
+the process with protocols and reference implementations.
 
@@
 projects)
+
+- Packaging tools
 
@@
 
-\subsection{Starging a Run}
+\subsection{Starting a Run}
 
@@
 
-\subsection{Requires Resource Resolution}
+\subsection{Resource Resolution}
 
-\subsection{Packaging}
+\subsection{Model Testing}
+
+\subsection{Packaging and Distribution}
 
@@
 
+- Workshops
+- User feedback
+
 \subsection{Packages}
 
+- slim, object-detection, mnist, hello
+
 \subsection{Early Use}
+
+\section{Summary}
 

### 2018-09-27 paper.tex
Wip

@@
 algorithm while a human authored program is written manually.
+
+While models may be represented in part by traditional installable
+software---e.g. a TensorFlow program that imperatively defines a model
+graph structure when run---models require more to be construed as
+reusable code: \emph{models must be trainable on novel data}.
+
+Table \ref{software-vs-models} compares traditional software with
+reusable models.
+
+\begin{table}[h!]
+  \begin{center}
+    \caption{Traditional software vs reusable models.}
+    \label{software-vs-models}
+    \begin{tabular}{l|l}
+      Traditional software & Installed code
+      Reusable models & Installed code + trainable on novel data
+    \end{tabular}
+  \end{center}
+\end{table}
+
+The remainder of this paper will outline an approach to package
+management applied to machine learning models that incorporates
+\emph{model operations} and \emph{run management} as a central enabler
+of model code reuse.
 

### 2018-09-27 paper.tex
Wip

@@
 \usepackage{hyperref}
+\usepackage{listings}
+
+\lstset{
+  basicstyle=\footnotesize\ttfamily,
+  breaklines=true,
+  captionpos=b,
+  framextopmargin=5pt,
+  framexbottommargin=5pt,
+  frame=tb
+}
 
@@
 
-Table \ref{software-vs-models} compares traditional software with
-reusable models.
-
-\begin{table}[h!]
-  \begin{center}
-    \caption{Traditional software vs reusable models.}
-    \label{software-vs-models}
-    \begin{tabular}{l|l}
-      Traditional software & Installed code
-      Reusable models & Installed code + trainable on novel data
-    \end{tabular}
-  \end{center}
-\end{table}
-
-The remainder of this paper will outline an approach to package
-management applied to machine learning models that incorporates
-\emph{model operations} and \emph{run management} as a central enabler
-of model code reuse.
-
-TODO:
-
-- What problem is being solved?
-
-Need to define reuse. Start with traditional softwar reuse and make it
-clear that Guild addresses model reuse. What is model reuse?
-
-- How package managers facilitate code reuse
-
-Apply analogy of system packaging and the importance of formalizing
-the process with protocols and reference implementations.
+The remainder of this paper will outline an approach to package that
+incorporates \emph{model operations} and \emph{run management} as a
+central enabler of code reuse for machine learning models.
 
@@
 
-- How machine learning models are distributed today (pip, GitHub
-projects)
+\subsubsection{Model zoos}
 
-- Packaging tools
+A common approach to sharing and reusing machine learning models is a
+\emph{model zoo}---an online repository of reusable models that
+includes source code, examples, documentation, and in some cases
+pretrained models. The \href{Caffe Model Zoo}{Caffe Model Zoo} was one
+of the first model zoos and has inspired serveral others (ref).
 
-- Frameworks and libraries
+Model zoos encourage code reuse by consolidating related models
+(e.g. based on underlying library implementation or application
+domain) and providing consistent documentation and repeatable methods
+for using the models.
 
-- TensorFlow Hub
+Model zoos, however, do not typically provide tools for packaging,
+distributing, and using models, beyond those of publishing source code
+and documentation (e.g. GitHub, web sites, etc.)
 
-- Keras Applications
+\subsubsection{TensorFlow Hub and Keras Applications}
 
-- ???
+\href{https://www.tensorflow.org/hub/}{TensorFlow Hub modules} and
+\href{https://keras.io/applications/}{Keras Applications} are examples
+of framework level facilities that provide a higher degree of model
+reuse vis-\'a-vis model zoos. Both TensorFlow Hub modules and Keras
+application support tools and patterns for packaging, distributing,
+and using model source code and associated pretrained models. They
+emphasize the use of \emph{transfer learning} where applicable for
+training models on novel datasets.
+
+\subsubsection{Software packages and source coderepositories}
+
+Models are commonly reused through traditional software distribution
+channels: packages and source code repositories. In both cases, model
+source code is provided along with varying levels of documentation and
+supporting tools. Unlike model zoos and framework packages, there is
+little consistency in quality of code reuse available through these
+channels. Developers are left to their own accord to find and use
+available models.
 
@@
 
-- How is Guild different from these cited projects?
+Guild AI combines elements from model zoos, framework packages, and
+traditional software channels to provide a state of the art facility
+for packaging, distributing and using machine learning models.
 
-- Include model and operation definitions
+As with model zoos, users can discover Guild AI models, including
+documentation on their use. Guild AI additionally supports
+installation and direct use of models through operations.
 
-- Reuse through distribution and patching
+Guild AI superficially resembles TensorFlow Hub in that users can
+discover, install, and use models quickly and easily. Guild AI however
+differs considerably in its implementation. Guild AI does not present
+a language level interface but instead defines a set of conventions
+that are supported through configuration. Guild AI packaging
+facilities can be applied to any machine learning model
+implementation.
 
-- Federation (protocol driven, intelligence moved to the perimeter).
+Guild AI also supports the well established practice of package
+maintenence, where a third party can create usable packages without
+necessarily coordinating with model developers. This is discussed in
+detail in Section \ref{sec:package-maintainer}.
+
+As with traditional software packages and source code repositories,
+Guild AI supports a federated approach to software distriution. Users
+are free to use Guild AI to create and distribute reusable models in a
+variety of ways. Refer to Section \ref{sec:use-cases} for coverage of
+various use case.
 
@@
 
+This paper relies on a number of core concepts, which are defined
+below.
+
 \subsection{Projects}
+
+A \emph{project} is a directory that contains model related
+code. Model developers maintain projects for their models. Model users
+maintain projects for the code that works with models, possibly
+training them or otherwise incorporating them into an application.
+
+Projects are central to model development and use. Guild AI supports
+project based workflow as described in Section
+\ref{sec:streamline-workflow}.
+
+\subsection{Guild File}
+
+A \emph{Guild file} is a plain text file containing Guild AI related
+configuration. The file is named \verb|guild.yml| and is typically
+located in the root directory of a Guild AI enabled project.
+
+Figure \ref{fig:guild-file} illustrates a simple Guild file.
+
+\begin{figure}
+{\footnotesize
+\begin{verbatim}
+ model: mnist
+ description:
+   Logistic regression classifier
+   of MNIST digits
+ operations:
+   train:
+     main: train_mnist
+     flags:
+       batchs-size: 32
+       train-steps: 1000
+   evaluate:
+     main: eval_mnist
+\end{verbatim}}
+\caption{Guild file example}
+\label{fig:guild-file}
+\end{figure}
 
@@
 
+A Guild AI \emph{package} is a Python wheel distribution (ref) that
+was generated using the \verb|guild package| command. Guild AI
+packages are no different from standard Python wheel distributions and
+are generated using \verb|setuptools|. However, they contain Guild AI
+specific entry points that effectively publish the models they
+contain.
+
 \subsection{Models}
 
+A \emph{model} in Guild AI is a representation of a machine learning
+model that is defined in a Guild file. Models define \emph{operations}
+(Section \ref{sec:operations}) that perform model related tasks such
+as training or evaluating as well as \emph{resources} (Section
+\ref{sec:resources}) that operations may require.
+
+Models may be defined according to the underlying architecture or
+intended use of the model. Guild AI does not prescribe any formal
+meaning to the term \emph{model} or what operations are supported.
+
 \subsection{Operations}
+\label{sec:operations}
+
+An \emph{operation} is an action that can be performed on a
+model. Operations are part of a model definition.
+
+Guild AI does not prescribe any particular set of operations that must
+be defined for a model. Model developers are free to name operations
+as they see fit, though Guild AI does encourage naming conventions.
+
+The \verb|train| operation---the act of training a model from
+scratch---for example, is an operation that most models
+support. However, the \verb|transfer-learn| operation---the act of
+transfering knowledge learned in one domain to another domain---is a
+form of training, but frequently appears in Guild AI models as an
+operation distinct from \verb|train|.
 
@@
 
+\emph{Flags} are parameters that can be set or modified by users when
+they run an operation. Flags are used as inputs to the underlying code
+that implements an operation.
+
 \subsection{Resources}
+\label{sec:resources}
+
+A Guild AI \emph{resource} represents a set of source files that can
+be made available as inputs to a model operation. Resources play a key
+role in Guild AI's ability to effective use models. Resources can be
+used to resolve project files, download files from URLs, unpack
+archives, and reference files generated by other operation.
+
+Figure \ref{fig:resource} illustrates a resource definition for a
+model. The resource \verb|idx-data| defines four source files that
+will be made available to any operation that requires that resource.
+
+\begin{figure}
+{\footnotesize
+\begin{verbatim}
+ model: mnist
+ resources:
+   idx-data:
+     description:
+       MNIST dataset in compressed
+       IDX format
+     sources:
+       - train-images-idx3-ubyte.gz
+       - train-labels-idx1-ubyte.gz
+       - t10k-images-idx3-ubyte.gz
+       - t10k-labels-idx1-ubyte.gz
+\end{verbatim}}
+\caption{Model resource example}
+\label{fig:resource}
+\end{figure}
 
@@
 
+A \emph{run} is a file system artifact---specifically a directory
+created and managed by Guild AI---that contains metadata and files
+generated by an operation. A run may also refer to the operation
+system process associated with a running operation.
+
+Runs are described in detail in Section \ref{sec:runs}.
+
 \subsection{Environments}
+
+Guild AI supports \emph{environments}, which are isolated runtime
+environments used for installing and using models. Guild AI supports
+environments created using
+\href{https://virtualenv.pypa.io}{\emph{virtualenv}}.
 
@@
 
+Guild AI \emph{workflows} are patterns of model use that are enabled
+by running operations in specific order. Worflows are not currently
+formal constructs in Guild AI but are referenced by convention or
+documented usage.
+
 \section{Use Cases}
+\label{sec:use-cases}
 
-\subsection{Publish a Model for Reuse}
+The package management facilities in Guild AI enable a number of use
+cases, which are described below. In each case, the following roles
+may be referenced:
+
+\begin{description}
+    \item[user] person using a model developed by someone else
+    \item[developer] person developing a model, either from scratch or
+      adapting the work of others
+    \item[packager] person neither using nor developing a model but
+      who packages models from developers for use by users
+\end{description}
+
+\subsection{Publish a Model for Use}
+
+A developer may encourage others to use her model by documenting the
+steps needed to install, adapt, and use it. She may be motivated to
+simplify the user experience so that her work is more easily and
+succesfully applied. The benefit to her may be quality feedback from
+expert users, improved reputation, a sense of contribution, or her
+colleagues may simply expect that work be documented and easy to use.
+
+While documenting the steps needed to use a model is undoubtedly
+helpful, the process is still burdensome for both the developer and
+her users. Guild AI can be used to simultaenously document model use
+but also directly support its use through model operations.
+
+Consider these instructions for model use, which might be documented
+for a project:
+
+{\footnotesize
+\begin{verbatim}
+1. Install required packages
+2. Download the raw data
+3. Prepare the raw data for training
+4. Train the model
+5. Export the trained model for deployment
+\end{verbatim}}
+
+While these steps provide invaulable information, they still rely on
+the user to carefully execute them and troubleshoot issues as they
+arise. The process, while thoroughly documented, can take time and is
+subject to error at any step.
+
+Guild AI can be used to both document and automate these
+steps. Listing~\ref{lst:published-model} illustrates a Guild file that
+might be used to codify the steps as model operations, which are both
+discoverable and runnable.
+
+\begin{lstlisting}[caption=whatever,label={lst:published-model}]
+model: sample
+operations:
+  prepare-data:
+    description:
+      Prepare data for training
+    main: prepare_data
+    requires: raw-data
+  train:
+    description: Train model
+    main: train
+    requires: prepared-data
+  export:
+    description:
+      Export model for deployment
+    main: export
+    requires: trained-model
+resources:
+  raw-data:
+    description: Raw data for training
+    sources:
+      - url: http://mydata.com/raw.tgz
+  prepare-data:
+    description: Prepared data
+    sources:
+      - operation: prepare-data
+  trained-model:
+    description: Trained model
+    sources:
+      - operation: train
+\end{lstlisting}
 
@@
 \subsection{Package Third Party Models}
+\label{sec:package-maintainer}
 
@@
 \subsection{Streamline Model Developer Workflow}
+\label{sec:streamline-workflow}
 
@@
 \section{Managing Runs}
+\label{sec:runs}
 
@@
 
+Table \ref{software-vs-models} compares traditional software with
+reusable models.
+
+\begin{table}[h!]
+  \begin{center}
+    \caption{Traditional software vs reusable models.}
+    \label{software-vs-models}
+    \begin{small}
+      \begin{tabular}{l|l}
+        \toprule
+        \textbf{Traditional software} & Installed code \\ \hline
+        \textbf{Reusable models} & Installed code + trainable on novel data \\
+        \bottomrule
+      \end{tabular}
+    \end{small}
+  \end{center}
+\end{table}
+
 \subsection{Citations}

### 2018-09-27 paper.tex
Wip

@@
 \lstset{
+  aboveskip=12pt,
   basicstyle=\footnotesize\ttfamily,
@@
   captionpos=b,
+  frame=tb,
+  framexbottommargin=5pt,
   framextopmargin=5pt,
-  framexbottommargin=5pt,
-  frame=tb
 }
@@
 
-Figure \ref{fig:guild-file} illustrates a simple Guild file.
+Listing~\ref{lst:guild-file} illustrates a simple Guild file.
 
-\begin{figure}
-{\footnotesize
-\begin{verbatim}
+\begin{lstlisting}[
+    caption=Simple Guild file example,
+    label={lst:guild-file}]
 model: mnist
@@
     main: eval_mnist
-\end{verbatim}}
-\caption{Guild file example}
-\label{fig:guild-file}
-\end{figure}
+\end{lstlisting}
 
@@
 
-Figure \ref{fig:resource} illustrates a resource definition for a
+Listing~\ref{lst:resource} illustrates a resource definition for a
 model. The resource \verb|idx-data| defines four source files that
@@
 
-\begin{figure}
-{\footnotesize
-\begin{verbatim}
+\begin{lstlisting}[
+    caption=Model resource example,
+    label={lst:resource}]
 model: mnist
@@
       - t10k-labels-idx1-ubyte.gz
-\end{verbatim}}
-\caption{Model resource example}
-\label{fig:resource}
-\end{figure}
+\end{lstlisting}
 
@@
     \item[packager] person neither using nor developing a model but
-      who packages models from developers for use by users
+      who packages models created by developers for use by users
 \end{description}
@@
 \subsection{Publish a Model for Use}
+\label{sec:publish-model}
 
-A developer may encourage others to use her model by documenting the
-steps needed to install, adapt, and use it. She may be motivated to
-simplify the user experience so that her work is more easily and
-succesfully applied. The benefit to her may be quality feedback from
-expert users, improved reputation, a sense of contribution, or her
-colleagues may simply expect that work be documented and easy to use.
+A \emph{developer} may encourage others to use her model by
+documenting the steps needed to install, adapt, and use it. She may be
+motivated to simplify the user experience so that her work is more
+easily and succesfully applied. The benefit to her may be quality
+feedback from expert users, improved reputation, a sense of
+contribution, or her colleagues may simply expect that work be
+documented and easy to use.
 
@@
 
-{\footnotesize
-\begin{verbatim}
-1. Install required packages
-2. Download the raw data
-3. Prepare the raw data for training
-4. Train the model
-5. Export the trained model for deployment
-\end{verbatim}}
+\begin{enumerate}
+   \item Install required packages
+   \item Download the raw data
+   \item Prepare the raw data for training
+   \item Train the model
+   \item Export the trained model for deployment
+\end{enumerate}
 
@@
 the user to carefully execute them and troubleshoot issues as they
-arise. The process, while thoroughly documented, can take time and is
-subject to error at any step.
+arise. The process takes time and is subject to error at any step.
 
@@
 steps. Listing~\ref{lst:published-model} illustrates a Guild file that
-might be used to codify the steps as model operations, which are both
-discoverable and runnable.
+might be used to codify the steps as model operations.
 
-\begin{lstlisting}[caption=whatever,label={lst:published-model}]
+\begin{lstlisting}[
+    caption=Sample project Guild file,
+    label={lst:published-model}]
 model: sample
@@
     requires: prepared-data
-  export:
+  export-model:
     description:
       Export model for deployment
-    main: export
+    main: export_model
     requires: trained-model
@@
 
+The operations can be run using the Guild AI command line interface as
+follows:
+
+{\footnotesize
+\begin{verbatim}
+ $ guild run prepare-data
+ $ guild run train
+ $ guild run export-model
+\end{verbatim}}
+
+Furthermore, Guild AI provides model help, detailing available
+operations, supported flags, and operation dependencies.
+
+A user can get help for the model by running:
+
+{\footnotesize
+\begin{verbatim}
+ $ guild help
+\end{verbatim}}
+
+Documentation is automatically generated from the model description,
+making Guild AI models self documenting.
+
+The developer can chose to distribute her model as a
+project---e.g. making it available as a GitHub repository. She may
+alternatively package the model and deploy as an installable Python
+wheel distribution artifact.
+
 \subsection{Use a Published Model}
+
+The flip side of the use case outline in
+Section~\ref{sec:publish-model} is that of the \emph{user}. A user is
+interesting in taking the work of a model developer and applying it,
+either by adapating her model to a new application or by integrating
+it as into another project.
+
+Users commonly rely on thorough documentation to effectively use
+models. If a project is under documented or otherwise hard to work
+with, it may not be used. This is a lost opportunity for both user and
+developer that hinders adoption and model improvement.
+
+As described in Section~\ref{sec:publish-model}, a published model is
+simple to use. From the standpoint of the user, the model can be used
+either by cloning the project repository---e.g. as in the case of
+GitHub published models---or install the model as a Python
+package. Assuming the project was published as a package named
+\verb|sample-project|, the user might run these commands to use the
+model:
+
+\setlength{\parindent}{1em}
+
+{\footnotesize\emph{Install the package}}
+
+{\footnotesize
+\begin{verbatim}
+ $ guild install sample-project
+\end{verbatim}}
+
+{\footnotesize\emph{View package help}}
+
+{\footnotesize
+\begin{verbatim}
+ $ guild help sample-package
+\end{verbatim}}
+
+{\footnotesize\emph{Use the model}}
+
+{\footnotesize
+\begin{verbatim}
+ $ guild run sample:prepare-data
+ $ guild run sample:train
+ $ guild run sample:export-model
+\end{verbatim}}
+
+\setlength{\parindent}{0em}
+
+This illustrates the usefulness of packaging models for
+reuse. Packaged models in this case consist of more than the
+underlying model code---they include additional information that makes
+them trivial to use relative to traditional forms of model reuse.
 
@@
 
+Complex software ecosystems such as GNU/Linux have formalized the role
+of a software \emph{packager} (or \emph{package maintainer}). The goal
+of a packager is to improve the value of a software distribution by
+creating high quality software packages that users find
+useful. Packers are often independent of the upstream software
+projects they package, serving as intermediaries betweeen the software
+developers and distribution users.
+
+Guild AI supports this pattern by allowing packagers to incorporate
+upstream model sources into Guild packages, patching them as needed to
+provide the desired functionality to users.
+
+Consider a case where a model developer is overloaded with research
+tasks and doesn't have time to provide documentation for using her
+models or publishing them for use as described in
+Section~\ref{sec:publish-model}. An independent \emph{packager} may
+step up to create a package instead.
+
+A packager must assume that upstream sources are available \emph{as
+  is} and he cannot expect developers to fix bugs or add new features
+(though he may certainly ask and hope). Packagers therefore must be
+prepared to \emph{patch} model code as needed to get it to work as
+expected.
+
+Guild AI provides various means of patching model source to support
+packagers in this role.
+
 \subsection{Team Collaboration}
+
+The roles of \emph{developer}, \emph{user}, and \emph{packager} often
+exist within a single organization or team. Guild AI supports team
+collaboration by supporting each role as a separate concern.
+
+Within a typical organization structure, the roles map as follows:
+
+\setlength{\parindent}{1em}
+developer $\rightarrow$ \emph{research scientist}
+
+user $\rightarrow$ \emph{software engineer}
+
+packager $\rightarrow$ \emph{research engineer}
+\setlength{\parindent}{0em}
+
+Of course this is a rough mapping and not all organizations share this
+structure. Whatever the job titles and division of labor, Guild AI
+supports the three facets of collaboration: model development, model
+use, and intermediation between those two points in the interest of
+freeing up developer time and resources to focus on pure model
+development.
 
@@
 \label{sec:streamline-workflow}
+
+In the case of a single developer who has no interest in publishing
+models or otherwise supporting users, Guild AI model abstractions
+provide value. By implementing models as units of operations, as is
+the case with Guild AI model packaging, developers ensure their models
+are easy to use from the early stages of development. This streamlines
+the development process as developers can repeatedly run and iterate
+through model operations using high level commands with well defined,
+self documenting interfaces.
 

### 2018-09-27 paper.tex
Wip

@@
 \subsection{Use a Published Model}
+\label{sec:use-model}
 
@@
 provide value. By implementing models as units of operations, as is
-the case with Guild AI model packaging, developers ensure their models
-are easy to use from the early stages of development. This streamlines
-the development process as developers can repeatedly run and iterate
-through model operations using high level commands with well defined,
-self documenting interfaces.
+the case with Guild AI model publishing, developers ensure their
+models are easy to use from the early stages of development. This
+streamlines the development process as developers can repeatedly run
+and iterate through model operations using high level commands with
+well defined, self documenting interfaces.
 
@@
 
+The final use case discussed involves managing tracking run artifacts.
+During both model development and use, it's useful to formally manage
+the artifacts both generated and consumed by model operation. This is
+similar to source code revision control, where developers can move
+backward and forward in time to view their work. In the case of Guild
+AI, the revisions are the results of data preparation, training
+experiments, model optimizations---anything that might be generated by
+an operation.
+
+Section~\ref{sec:runs} provides more details about Guild AI run
+management.
+
 \section{Using Models}
 
+Section~\ref{sec:use-model} describes the case of using published
+models. This section provides more details on model usage in Guild AI.
+
 \subsection{Packaged Models}
+
+Packaged models are models that have been bundles with supporting code
+and metadata into a Python wheel distribution. To generate a package,
+a developer or packager must include a \verb|package| definition in
+the project Guild file and then run the \verb|guild package| command.
+
+Listing~\ref{lst:package} contains a sample \verb|package| definition.
+
+\begin{lstlisting}[
+    caption=Sample package definition,
+    label={lst:package}]
+package: sample-project
+version: 1.0
+description: Sample packaged project
+url: https://my.co/packages/sample
+author: John Doe
+author-email: john@my.co
+license: Apache 2.0
+requires: [keras, Pillow, matlab]
+\end{lstlisting}
+
+Given a Guild file with such a package definition, Guild AI will
+generate a Python wheel distribution that can be used to install any
+models defined in the package.
 
@@
 
-- What is a run (from an operation)
+A \emph{run} is a formally managed file system artifact generated by
+an operation. Runs may also refer to the operating system process
+associated with a running operation.
 
-- What is a run concretely (i.e. directory, etc.)
+Runs contain critical information for tracking and understanding what
+happened during an operation:
+
+\begin{itemize}
+\item Run metadata such as the associated model and operation, status,
+  start and stop times, operating system command and environment, and
+  resolved dependencies
+\item Output generated by the run---specifically the operating system
+  process standard output and standard error
+\item Files used by the operation (resolved resource sources)
+\item Files generated by the operation
+\end{itemize}
 
@@
 
+Runs are started using the \verb|guild run| command and referencing a
+model operation. Operations may be run with additional flag values
+provided on the command line in the format \verb|NAME=VALUE|.
+
+Here's an example of running an operation with flag values:
+
+{\footnotesize
+\begin{verbatim}
+ $ guild run mnist:train \
+     steps=10000 \
+     batch-size=64 \
+     learning-rate=0.0001
+\end{verbatim}}
+
 \subsection{Listing Runs}
+
+Runs may be listed using the \verb|guild runs| command. Runs are
+displayed with their unique ID, operation name, start time, status,
+and user label.
+
+Listed runs may be filtered by status, operation, and label.
 
@@
 
+Information about one or more runs may be displayed using the
+\verb|guild runs info| command. By default, high level run information
+such as the run ID, operation, start time, command, exit status, and
+operting system pid are displayed. Additional command options may be
+used to view more run information including files, flag values,
+dependencies, and operation output.
+
 \subsection{Deleting Runs}
 
-\subsection{Archiving and Restoring Runs}
+One or more runs may be deleted using the \verb|guild runs rm|
+command. Runs may be deleted using status, operation, or label.
 
-\subsection{Run Dependencies}
-
-\subsection{Remote Runs}
+Guild AI will restore deleted runs with \verb|guild runs restore| and
+permanently delete runs using \verb|guild runs purge|.
 
@@
 
+\subsection{Testing models}
+
 \subsection{Packaging}
@@
 
-- Core - written in Python, etc.
+Guild AI is written in the Python programming language. It makes use
+of a number of excellent open source libraries, many of which are
+listed below.
 
@@
 
+Guild AI is primarily a command line tool. Users type Guild AI
+commands in the form:
+
+{\footnotesize
+\begin{verbatim}
+guild COMMAND [ARG]...
+\end{verbatim}}
+
+Guild AI makes use of the Click Python library (ref) to implement its
+core command line processingn support.
+
 \subsection{Configuration Processing}
+
+Guild AI supports YAML (ref) as its configuration language for both
+Guild files and user configuration. It uses the PyYAML Python library
+(ref) for low level parsing.
+
+Guild AI has implemented a novel scheme for configuration reuse, which
+supports multiple inheritance, file includes, and section
+includes. The reuse support allows Guild AI developers to maintain
+complex model configurations with easily managed abstractions.
 
@@
 
+Guild AI implements its own resource resolution scheme, which is used
+to setup runs with required resource sources. Guild makes use of
+directed acyclical graphs (DAGs) to model and efficiently resolve
+complex interdependencies across operation.
+
 \subsection{Model Testing}
+
+Guild AI supports model testing through a novel configuration scheme
+that integrates with model definitions. Tests may be defined for one
+or more models, each running and verifying one or more operations.
 
@@
 
+Guild AI packages are valid Python wheel distributions. The underlying
+libraries used to install Guild packages are the same as those used by
+the \verb|pip| pgrogram to install PyPI packages. As a result, Guild
+AI can be used to install PyPI packages and pip can be used to install
+Guild AI packages---the process is the same in both cases.
+
 \subsection{Run Indexing}
+
+Guild AI uses a run indexing scheme to optimize run queries when
+comparing runs and uses the Whoosh Python library (ref) in support
+that.
 
@@
 
-\subsection{Remote Environments}
+Guild AI provides various visualization tools, including its own run
+viewer (Guild View) and integration with TensorBoard (ref).
+
+Guild View is impemented using the VueJS library (ref) for the front
+end and Werkzeug (ref) for the HTTP API back end.
 
@@
 
-- Apache 2.0
+Guild AI is freely available under the Apach 2.0 open source
+license. It has been under active development for the last two years
+and undergone significant revision and updates during that time based
+on user feedback and real world application development.
 

### 2018-09-28 paper.tex
Wip

@@
   framextopmargin=5pt,
+}
+
+\usepackage{enumitem}
+
+\setlist[description]{
+  itemsep=4pt,
+  labelindent=1em,
+  leftmargin=1em,
+  topsep=4pt,
+}
+
+\setlist[enumerate]{
+  itemsep=4pt,
+  topsep=4pt,
+}
+
+\setlist[itemize]{
+  itemsep=4pt,
+  topsep=4pt,
 }
@@
 have different contexts. In the most general context, models are
-mathematical concepts or language that represents a system
-(needref). In the context of machine learning, models may be
-represented by computer source code, either explicitly as declared
-structures, or implicitly by way of executable instructions that
-perform model related tasks. A \emph{trained model} is a model that
-has learned some representation of a system through the process of
-computer based optimization.
+mathematical concepts or language that represents a system (ref). In
+the context of machine learning, models may be represented by computer
+source code, either explicitly as declared structures, or implicitly
+by way of executable instructions that perform model related tasks. A
+\emph{trained model} is a model that has learned some representation
+of a system through the process of computer based optimization.
 
 For the purpose of our discussion, a machine learning model is a
-software representation of a specific mathetical concept that can be
+software representation of a specific mathematical concept that can be
 trained by a computer. Models may be in various states:
@@
 pretrained models. The \href{Caffe Model Zoo}{Caffe Model Zoo} was one
-of the first model zoos and has inspired serveral others (ref).
+of the first model zoos and has inspired several others (ref).
 
@@
 
-\subsubsection{Software packages and source coderepositories}
+\subsubsection{Software packages and source code repositories}
 
@@
 Guild AI also supports the well established practice of package
-maintenence, where a third party can create usable packages without
+maintenance, where a third party can create usable packages without
 necessarily coordinating with model developers. This is discussed in
@@
 As with traditional software packages and source code repositories,
-Guild AI supports a federated approach to software distriution. Users
+Guild AI supports a federated approach to software distribution. Users
 are free to use Guild AI to create and distribute reusable models in a
@@
     flags:
-      batchs-size: 32
+      batch-size: 32
       train-steps: 1000
@@
 
-The \verb|train| operation---the act of training a model from
-scratch---for example, is an operation that most models
-support. However, the \verb|transfer-learn| operation---the act of
-transfering knowledge learned in one domain to another domain---is a
-form of training, but frequently appears in Guild AI models as an
-operation distinct from \verb|train|.
+Below are some common operation names:
+
+\begin{description}
+\item[prepare] prepare a dataset for training
+\item[train] train a model from scratch
+\item[transfer-learn] train a model using transfer learning
+\item[finetune] finetune a trained model
+\item[evaluate] evaluate a model
+\item[classify] use a trained model to classify inputs
+\item[compress] compress a trained model (e.g. using quantization,
+  etc.)
+\item[export-and-freeze] export a frozen inference
+  graph\footnote{TensorFlow specific}
+\item[tflite] generate a TF Lite file from a frozen
+  model\footnotemark[\value{footnote}]
+\end{description}
+
+This list illustrates that model operations can be used to perform a
+host of tasks beyond training and evaluation. In fact, well designed
+models can encompass all of the operations associated with a machine
+learning application development pipeline, from data acquisition and
+preparation to application deployment and monitoring.
 
@@
 that implements an operation.
+
+Below is an example of using a flag to set the \emph{learning rate}
+for a \emph{train} operation.
+
+{\footnotesize
+\begin{verbatim}
+ $ guild run train learning-rate=0.0001
+\end{verbatim}}
 
@@
   adapting the work of others
-    \item[packager] person neither using nor developing a model but
-      who packages models created by developers for use by users
+\item[packager] person neither using nor developing a model but who
+  packages models created by developers for use by users
 \end{description}
@@
 motivated to simplify the user experience so that her work is more
-easily and succesfully applied. The benefit to her may be quality
+easily and successfully applied. The benefit to her may be quality
 feedback from expert users, improved reputation, a sense of
@@
 helpful, the process is still burdensome for both the developer and
-her users. Guild AI can be used to simultaenously document model use
+her users. Guild AI can be used to simultaneously document model use
 but also directly support its use through model operations.
@@
 
+\setlength{\parindent}{1em}
 \begin{enumerate}
@@
 \end{enumerate}
-
-While these steps provide invaulable information, they still rely on
+\setlength{\parindent}{0em}
+
+While these steps provide invaluable information, they still rely on
 the user to carefully execute them and troubleshoot issues as they
@@
 interesting in taking the work of a model developer and applying it,
-either by adapating her model to a new application or by integrating
+either by adapting her model to a new application or by integrating
 it as into another project.
@@
 useful. Packers are often independent of the upstream software
-projects they package, serving as intermediaries betweeen the software
+projects they package, serving as intermediaries between the software
 developers and distribution users.
@@
 
-Given a Guild file with such a package definition, Guild AI will
-generate a Python wheel distribution that can be used to install any
-models defined in the package.
+Given a Guild file with a package definition, develolpers can use
+Guild AI to generate a Python wheel distribution, which in turn can be
+used by users to install package models. Developers can also upload
+packages to PyPI to make the package available for search and
+installation.
+
+Guild AI models are installed like any other Python package. Users may
+use Guild AI to install the package:
+
+{\footnotesize
+\begin{verbatim}
+ $ guild install sample-project
+\end{verbatim}}
+
+Alternatively, a user may use pip:
+
+{\footnotesize
+\begin{verbatim}
+ $ pip install sample-project
+\end{verbatim}}
+
+Guild AI package requirements may be included in requirements files
+(e.g. \verb|requirements.txt|) or as dependencies of other Python
+package distributions.
+
+Package models are convenient for using models and their related
+functionality when a user doesn't need to modify the model source
+code. To use models and also have the option of modifying their source
+code, a user should use project models (Section
+\ref{sec:project-models}).
 
 \subsection{Project Models}
+\label{sec:project-models}
+
+Project models are defined in a project Guild file---i.e. a file named
+\verb|guild.yml| that resides in the top level of a projet
+directory. Users may run operations on project models by running them
+from within the project directory or by refering the project directory
+in the operation specified for the \verb|run| command.
+
+Project models are used by users or developers who expect to modify
+project files.
+
+Unlike packaged models, project models do not need to be installed
+using a command---they are available from the project itself. A user
+need only change to the project directory to run model operations.
 
@@
 
+A user may list available models using the \verb|guild models|
+command. This command lists packaged models and, if the command is run
+within a project, project models.
+
+Each model has one or more operations, which can be listed using the
+\verb|guild ops| command.
+
+The ability to discover available models and operations is a key
+feature enabling model use in Guild AI. Without formally defining
+these, users are left to their own to infer model capabilities from
+available documentation and source code.
+
 \subsection{Getting Help for Models}
 
+A user may use the \verb|guild help| command to get details about a
+model, its operations, operation flags, and resource
+dependencies. This is similar to the \emph{man} facility (ref) on many
+systems.
+
+A user may also get help for a particular operation by using the
+\verb|--help-op| option with the \verb|guild run| command. This is
+similar to the \verb|--help| option available for many programs.
+
+Figure~\ref{fig:op-help} contains sample help for the \verb|train|
+operation of the \verb|gpkg.mnist/cnn| package model.
+
+\begin{figure}
+  \begin{lstlisting}[]
+  Usage: guild run [OPTIONS] cnn:train
+  [FLAG]...
+
+  Train the CNN
+
+  Use 'guild run --help' for a list of
+  options.
+
+  Dependencies:
+    mnist-dataset  Yann Lecun's MNIST
+                   dataset in compressed
+                   IDX format
+
+  Flags:
+    batch-size  Number of images to
+                include in a training
+                batch (100)
+    epochs      Number of epochs to train
+                (10)
+  \end{lstlisting}
+  \caption{Sample operation help}
+  \label{fig:op-help}
+\end{figure}
+
+It is important to note that model and operation help is automatically
+generated from model descriptions. This facility lowers the cost of
+model documentation for developers and gives users a consistent
+interface for discovering model capabilities and intructions for using
+them.
+
 \subsection{Running Operations}
 
+Once a model is available---either as an installed package model or
+defined in a project---it can be used by running \emph{operations}. An
+operation is an action that can be performed on a model. Operations
+both \emph{define and implement} model capabilities. The act of using
+a model is the process of running operation.
+
+Operations may define an entire application development life cycle for
+one model or a host of models that work together.
+
+Section~\ref{sec:operations} lists common operation names.
+
+The act of running an operation starts a \emph{run}, which is both an
+operating process and a Guild AI managed file system artifact that
+contains run details including generated output.
+
+A user can run an operation using the \verb|guild run| command.
+
+Refer to Section~\ref{sec:runs} for information about managing runs.
+
 \subsection{Viewing and Comparing Runs}
 
-\subsection{Exporting Model Artifacts}
+As users and developers run model operations, they can view the
+results in various ways. Guild AI provides a comprehensive command
+line interface for managing runs, which is outlined in
+Section~\ref{sec:runs}.
+
+Guild AI also provides various methods for visualizing runs. Guild
+View is an application that is provided with Guild AI that launches a
+web application that can be used to view run details, including run
+files.
+
+Guild AI also integrates TensorBoard (ref) as a visualization tool,
+which can be used to view TensorFlow event logs that are generated by
+model operations.\footnote{Operations must explicitly write TensorFlow
+  event logs during a run to support TensorBoard visualization.}
+
+\subsection{Accessing Generated Artifacts}
+
+Operations generate \emph{artifacts}, which are Guild AI managed files
+stored on the local file system. Guild AI does not attempt to
+obfuscate generated artifacts---they are maintained in the run
+directory as written during the operation.
+
+Artifacts are routinely used as inputs to subsequent operations. For
+example, a TensorFlow checkpoint generated by a \verb|train| operation
+may be used as input to an \verb|export-and-freeze| operation, which
+in turn generates a frozen inference graph. This process is automatic
+and part of Guild AI's resource resolution process.
+
+Artifacts may also be accessed directly by users given their file
+system paths. A user can list the full paths for all files associated
+with a run using the \verb|guild runs info| command with the
+\verb|-ff| option. With these path, the user may copy the files or
+link to them as needed.
+
+Runs may also be \emph{exported} to a location using the
+\verb|guild export| command. Exported runs are copied (or moved, if
+the \verb|--move| option is specified) to a specified file system
+directory. This can be used to create backups or to transfer runs to
+another location.
 
@@
 such as the run ID, operation, start time, command, exit status, and
-operting system pid are displayed. Additional command options may be
+operating system pid are displayed. Additional command options may be
 used to view more run information including files, flag values,
@@
 Guild AI makes use of the Click Python library (ref) to implement its
-core command line processingn support.
+core command line processing support.
 
@@
 libraries used to install Guild packages are the same as those used by
-the \verb|pip| pgrogram to install PyPI packages. As a result, Guild
+the \verb|pip| program to install PyPI packages. As a result, Guild
 AI can be used to install PyPI packages and pip can be used to install
@@
 
-Guild View is impemented using the VueJS library (ref) for the front
+Guild View is implemented using the VueJS library (ref) for the front
 end and Werkzeug (ref) for the HTTP API back end.
@@
 
-Guild AI is freely available under the Apach 2.0 open source
+Guild AI is freely available under the Apache 2.0 open source
 license. It has been under active development for the last two years
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Typography}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Delete this to end of doc
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Verbatim}
-
-{\footnotesize
-\begin{verbatim}
-dvips -Ppdf -tletter -G0 -o paper.ps paper.dvi
-ps2pdf paper.ps
-another line yo
-\end{verbatim}}
-
-You can copy the file by running \verb|cp foo bar| where \textit{foo}
-is some file you want to copy and \textit{bar} is something else.
-
-\subsection{Italics}
-
-\textit{Proceedings of the $\mathit{2}^{nd}$ SysML Conference}
-
-And \emph{this is for emphasis!}
-
-\subsection{Bold}
-
-I will \textbf{make this bold} yo.
-
-\subsection{Teletype}
-
-Set the value to \texttt{accepted} and everything will be okay.
-
-\subsection{Dots}
-
-ldots: \ldots
-
-dots: \dots
-
-\subsection{Less than, greater than}
-
-\textless{}email@domain.com\textgreater{}
-
-\subsection{Footnotes}
-
-You can use footnotes\footnote{Footnotes should be complete
-  sentences.} which will be super awesome. Don't ask me how it works.
-
-\subsection{Tables}
-
-\begin{table}[t]
-  \caption{Classification accuracies for naive Bayes and flexible
-    Bayes on various data sets.}
-  \label{sample-table}
-  \begin{center}
-    \begin{small}
-      \begin{sc}
-        \begin{tabular}{lcccr}
-          \toprule
-          Data set & Naive & Flexible & Better? \\
-          \midrule
-          Breast    & 95.9$\pm$ 0.2& 96.7$\pm$ 0.2& $\surd$ \\
-          Cleveland & 83.3$\pm$ 0.6& 80.0$\pm$ 0.6& $\times$\\
-          Glass2    & 61.9$\pm$ 1.4& 83.8$\pm$ 0.7& $\surd$ \\
-          Credit    & 74.8$\pm$ 0.5& 78.3$\pm$ 0.6&         \\
-          Horse     & 73.3$\pm$ 0.9& 69.7$\pm$ 1.0& $\times$\\
-          Meta      & 67.1$\pm$ 0.6& 76.5$\pm$ 0.5& $\surd$ \\
-          Pima      & 75.1$\pm$ 0.6& 73.9$\pm$ 0.5&         \\
-          Vehicle   & 44.9$\pm$ 0.6& 61.5$\pm$ 0.4& $\surd$ \\
-          \bottomrule
-        \end{tabular}
-      \end{sc}
-    \end{small}
-  \end{center}
-  \vskip -0.1in
-\end{table}
-
-Table \ref{software-vs-models} compares traditional software with
-reusable models.
-
-\begin{table}[h!]
-  \begin{center}
-    \caption{Traditional software vs reusable models.}
-    \label{software-vs-models}
-    \begin{small}
-      \begin{tabular}{l|l}
-        \toprule
-        \textbf{Traditional software} & Installed code \\ \hline
-        \textbf{Reusable models} & Installed code + trainable on novel data \\
-        \bottomrule
-      \end{tabular}
-    \end{small}
-  \end{center}
-\end{table}
-
-\subsection{Citations}
-
-I really like TensorFlow \cite{tensorflow2015-whitepaper}.
-
 \bibliography{paper}

### 2018-09-28 paper.tex
Wip

@@
 Runs are described in detail in Section \ref{sec:runs}.
+
+\subsection{Run Directories}
+\label{sec:run-dir}
+
+A \emph{run directory} is a directory used for a run. During a run
+operation, the run directory is the system current working
+directory. Operations should write run artifacts within the current
+working directory to ensure that they are associated with the run.
+
+By default, Guild AI generates a new directory for each run and
+creates links to required resource sources within that directory. Once
+the directory is prepared, Guild AI starts the run operating system
+process, which then may access sources within the current working
+directory.
+
+Users may optionally specify an alternative run directory for a
+run. This is commonly used by model developers during the process of
+implementing model operation.s
 
@@
 
-\section{Developing Reusable Models}
+\section{Developing Models}
+
+As discussed above, published models---deployed from installed
+packages or as projects---can be used by running model
+\emph{operations}. Operations generate \emph{artifacts} that can be
+used in subsquent operations or as final outputs in an application
+development workflow.
+
+In this section we discuss how such models are created using Guild AI.
 
@@
 
-- How to choose a model boundary?
-
-- How to define operations
-
-\subsection{Customizing Models}
-
-\subsubsection{Model Inheritance}
-
-\subsubsection{Configuration Mixins}
-
-\subsubsection{Modifying Operations}
-
-\subsubsection{Modifying Flag Values}
+When developing a model from scratch, a developer may ask two
+questions:
+
+\begin{itemize}
+\item What is the defining characteristic of the model?
+\item What can users do with the model?
+\end{itemize}
+
+The answers to these questions will inform the decision of what to
+name the model and its operations. These values can be stubbed out in
+a Guild file to provide a scaffold for implementation.
+
+In many cases, this is simply a matter of selecting a model name and
+creating a \verb|train| operation. Listing~\ref{lst:pet-stub}
+illustrates a straightforward pet classifier.
+
+\begin{lstlisting}[
+    caption=Sample Guild file for a pet classifier,
+    label={lst:pet-stub}]
+model: pets
+description:
+  Pet classifier using a CNN
+operations:
+  train:
+    description: Train the classifier
+    main: train
+    flags:
+      images:
+        description:
+          Directory containing the pet
+          images to train
+        required: yes
+      epochs:
+        description:
+          Number of epochs to train
+        default: 100
+\end{lstlisting}
+
+With even a simple stub, a developer can formalize the model and what
+it does. This stage clarifies the model's user interface before the
+functionality is implemented.
+
+With a basic skeleton in place, the developer can implement model
+operations. In the case of the pet classifier
+(Listing~\ref{lst:pet-stub}) this means implementing training support
+in a file named \verb|train.py| that resides in the project directory.
+
+Operations can be developed and tested early on using Guild AI. Each
+time \verb|guild run| is used to test an operation, Guild AI generates
+a distinct, trackable run. Runs may be compared over time to help
+answer questions or resolve issues.
+
+Guild AI provides two additional mechanisms to help model developers
+implement operations. Both effect the \emph{run directory}
+(Section~\ref{sec:run-dir}) used by Guild AI.
+
+The first is the use the \verb|--run-dir| option
+to the \verb|guild run| command. This option may be used to specify an
+alternative directory for the run. This is helpful when the developer
+doesn't want to generate new runs for early stage opertion
+development.
+
+The second mechanism is the use of the \verb|--stage| option to the
+\verb|guild run| command. This option may be used to stage a run in an
+alternative directory without running the operation. This is helpful
+when the developer wants to study the run directory layout or to run
+low level commands or scripts during the development process.
+
+The developer can continue to evolve the model operations as needed to
+satisfy user requirements. This may include new operations or
+additional operation flags, which give users more flexibility when
+running an operation. The developer may similarly add new models to
+the Guild file.
+
+\subsection{Adapting Existing Model Code}
+
+In many cases, a developer will already have working model code she
+wants to incorporate into a formalized model definition. As with the
+role of \emph{packger} (Section~\ref{sec:package-maintainer}), a
+developer may even be required to work with upstream sources she
+cannot easily change. Guild AI provides a number of features that
+support the adaptation of existing model code into usable models.
+
+The operation \verb|main| attribute specifies a Python main module to
+run. In many cases, a developer can simply reference an existing
+Python script to incorporate it into an operation. In cases where a
+script doesn't already exist---for example, the model code is in a
+Jupyter Notebook and not readily usable---the developer should create
+a new script that contains the applicable model code and use it for an
+operation.
+
+Operation \emph{flags} specified in the form \verb|NAME=VALUE| as
+arguments to the \verb|guild run| command are passed to the Python
+main module as command line arguments in the form
+\verb|--NAME VALUE|. For example, assuming an operation \verb|train|
+with a main module \verb|train|, the command
+\verb|guild run train epochs=100| would be translated to the Python
+command \verb|python -m train --epochs 100|. In this way developers
+can parameterize scripts via operation flags.\footnote{It is standard
+  practice to use Python's argparse module to support named command
+  line options following the getopt convention (ref) in a Python
+  script.}
+
+If a flag name doesn't correspond to the option name expected
+(e.g. the train script expected the option \verb|num_epochs|) the
+developer can specify an alternative argument name for a flag using
+the \verb|arg-name| attribute.
+
+\subsection{Patching}
+
+In cases where a developer cannot modify upstream sources or chooses
+not to (e.g. to simplify ongoing mainteance) he may choose to patch
+model sources for use in a model. Guild AI supports two methods of
+patching.
+
+The first method is to run a post processing script on required model
+sources. This can be specified using a \verb|post-process| command for
+a model source that applies patch files to upstream sources. Guild AI
+will use the patched versions for related operations.
+
+The second method is to wrap upstream scripts and monkey patch (ref)
+the Python environment as needed to change behavior. An example of
+this can be found in the \verb|gpkg.slim| package, which patches the
+TensorFlow \verb|slim.losses.softmax_cross_entropy| module to add
+support for balanced weight training. This technique successfully adds
+a useful feature while avoiding the need to modify the upstream train
+support in TF Slim.\footnote{While one could argue that it would be
+  better to submit a pull request with the new functionality to
+  upstream authors, there are always cases where this is not an
+  option. Patching in these cases may be the only way to fix issues or
+  add features.}
+
+\subsection{Model Definition Reuse}
+
+Guild AI provides a number of features that support model definition
+reuse.
+
+\subsubsection{Configuration Inheritance}
+
+Guild files may contain \verb|config| section that contain arbitrary
+configuration, which can be inherited by
+models. Listing~\ref{lst:inheritance} defines two models, each
+inheriting the properties of shared config. The shared config
+\verb|model-base| defines the common model operations and uses
+\emph{parameters} to define a model name and default learning rate.
+
+\begin{lstlisting}[
+    caption=Configuration inheritance,
+    label={lst:inheritance}]
+- config: model-base
+  operations:
+    train:
+      main: train --model {{model-name}}
+      flags:
+        epochs: 100
+        learning-rate: {{default-lr}}
+
+- model: logreg
+  extends: model-base
+  params:
+    model-name: logreg
+    default-lr: 0.01
+
+- model: cnn
+  extends: model-base
+  params:
+    model-name: cnn
+    default-lr: 0.0001
+\end{lstlisting}
+
+Configuation inheritance can be applied across Guild files---e.g. to
+configuration defined in packages or other projects. This is useful
+for extending model definitions from other
+developers. Listing~\ref{lst:extend-slim} demonstrates how a model can
+inherit all of the operations of another model with a single line of
+configuration.
+
+\begin{lstlisting}[
+    caption=Extending PNASNet Mobile,
+    label={lst:extend-slim}]
+- model: my-classifier
+  extends: gpkg.slim.models/pnasnet-mobile
+\end{lstlisting}
+
+Configuration inheritance has proven effective at managing complex
+model configuration. This is evident in the \verb|gpkg.slim| and
+\verb|gpkg.object-detection| packages, which make extensive use of
+configuration inheritance to simplify their respective Guild files.
+
+\subsubsection{Configuration Includes}
+
+Configuration may also be reused by including shared configuration
+files using \verb|include| objects. Listing~\ref{lst:shared} and
+Listing~\ref{lst:include-shared} illustrate how includes can be used.
+
+\begin{lstlisting}[
+    caption=Shared configuration (e.g. defined in shared.yml),
+    label={lst:shared}]
+- config: model-base
+  operations:
+    train: train
+\end{lstlisting}
+
+\begin{lstlisting}[
+    caption=Use of includes (e.g. defined in guild.yml),
+    label={lst:include-shared}]
+- include: shared.yml
+
+- model: model-a
+  extends: model-base
+
+- model: model-b
+  extends: model-base
+\end{lstlisting}
+
+Includes may also be used to merge shared configuration into other
+configuration. Listing~\ref{lst:include-flags} illustrates how shared
+configuration can be included into operation flags. The special
+attribute \verb|$include| signifies that the corresponding value
+defined in the referenced config should be merged into the current
+value. The value for \verb|$include| can be a list to merge from
+multiple sources. In the example, the value for \verb|learning-rate|
+is redefined in the operation.
+
+\begin{lstlisting}[
+    caption=Including shared flag configuration,
+    label={lst:include-flags}]
+- config: default-train-flags
+  flags:
+    epochs: 100
+    batch-size: 32
+    learning-rate: 0.01
+
+- model: sample
+  operations:
+    train:
+      main: train
+      flags:
+        $include: default-train-flags
+        learning-rate: 0.001
+\end{lstlisting}
 
@@
 
+The final method of model definition reuse described is that of
+\emph{Python main module reuse}. Main modules---i.e. the modules
+referenced in an opertion \verb|main| specification---may reside in
+any installed Python package. To reuse the main module, a developer
+need only include the package reference in the main specification.
+
+Listing~\ref{lst:tflite_convert} illustates the use of the TensorFlow
+module \verb|tflite_convert| to generte a TF Lite file for an
+operation.
+
+\begin{lstlisting}[
+    caption=Reusing a Python main module,
+    label={lst:tflite_convert}]
+model: sample
+operations:
+  tflite:
+    main: tensorflow/contrib/lite/python/tflite_convert
+\end{lstlisting}
+
+Developers may create packages of reusable modules that can be easily
+used to implement model operations. For example, consider an
+organization that runs a specialized inference server that hosts
+models deployed using an HTTP POST interface. The model development
+team might create a package \verb|server-utils| that contains a Python
+main module \verb|server_utils.deploy| that performs the
+deployment.
+
+Listing~\ref{lst:deploy} illustrates how such a facility could be
+easily incorporated into a model to enable deployments. In the
+example, the model is defined in a package that requires the
+\verb|server-utils| package, which will be automatically installed by
+the command \verb|guild install classifiers|.
+
+\begin{lstlisting}[
+    caption=Quickly enabling model deploy,
+    label={lst:deploy}]
+- package: classifiers
+  requires: [server-utils]
+
+- model: resnet-classifier
+  operations:
+    train: resnet_train
+    deploy: server_utils.deploy
+    requires: trained-model
+  resources:
+    trained-model:
+      sources:
+        - operation: train
+\end{lstlisting}
+
 \subsection{Testing models}
@@
 \subsection{Packaging}
-
-\subsection{Patching Strategies}
 

### 2018-09-28 paper.tex
Wip

@@
 \begin{figure}
-  \begin{lstlisting}[]
+  \begin{lstlisting}
   Usage: guild run [OPTIONS] cnn:train
@@
 another location.
+
+\subsection{Isolating Runs Using Environments}
+
+The discussion of using models to this point has not mentioned
+\emph{environments} as environment are optional for using Guild
+AI. However, environments are useful for isolating installed packages
+and runs on a system.
+
+When running Guild AI operations in an activated environment, the
+following are environment specific:
+
+\begin{itemize}
+\item Installed packages and therefore installed models
+\item Runs
+\end{itemize}
+
+Environments are created using the \verb|guild init| command. Once
+created, an environment must be explicitly activated using the
+\verb|source guild-env| command.
+
+Environments are useful isolating project level work. It's not uncommon
+to have separate environments for each project.
 
@@
 
-\subsection{Testing models}
+\subsection{Testing}
+
+Users may trust that installed packages have undergone testing before
+they being published. The goal of managing machine learning models as
+packages, after all, is to ensure that models work as advertised. In
+support of this goal, Guild AI lets developers and packagers specify
+tests that can be used to model integrity.
+
+Listing~\ref{lst:tests} contains two tests: one that verifies model
+help---ensuring that what the user sees when she runs
+\verb|guild help| is what the developer intendes---and another that
+exercises model operations and checks results.
+
+\begin{lstlisting}[
+    caption=Model tests,
+    label={lst:tests}]
+- test: help
+  steps:
+    - compare-help: test/help
+- test: model
+  steps:
+    - run-op: prepare-samples
+      flags:
+        images: test/samples
+    - run-op: train
+      expected:
+        - file: checkpoint
+    - run-op: evaluate
+      expected:
+        - scalar: accuracy > 0.7
+\end{lstlisting}
+
+The model test runs three operations: prepare-samples, train, and
+evaluate. The train step asserts that a checkpoint file exist, which
+confirms that the operation successfully saved a checkpoint. The
+evaluate step asserts that the accuracy for the trained model is at
+least 0.7.
+
+Tests can be run using the \verb|guild test| command.
+
+Tests may be run on an ad hoc basis or as a continuous integration
+release process.
 
 \subsection{Packaging}
+
+Our final point of discussion on the topic of model development is
+\emph{packaging}. Packaging consists of generating a Python wheel
+distribution that contains the Guild file and all supporting project
+code. The generated wheel distribution may be distributed internally
+within an organization or published to PyPI.
+
+Packages that are published to PyPI can be installed using the command
+\verb|guild install| or using pip.
+
+Packages are convenient for installing
 

### 2018-09-28 paper.tex
Wip

@@
   topsep=4pt,
+  labelindent=1em,
+  leftmargin=1em,
 }
@@
 \begin{itemize}
-\item The Python module \verb|tensorflow| should be installed
+\item The Python module \verb|tensorflow| should be installed.
 \item Additional Python modules required by \verb|tensorflow| should
-  also be installed
-\item Installed software should work as expected on the target system
-\item At a future date \verb|tensorflow| may be similarly uninstalled along
-  with its no-longer-needed required packages
+  also be installed.
+\item Installed software should work as expected on the target system.
+\item At a future date \verb|tensorflow| may be similarly uninstalled
+  along with its no-longer-needed required packages.
 \item The act of installing and uninstalling \verb|tensorflow| should
   not break or otherwise destabilize other installed software on the
-  target system
+  target system.
 \end{itemize}
@@
 
+\begin{figure}
 \begin{lstlisting}[
@@
 \end{lstlisting}
+\end{figure}
 
@@
 \end{lstlisting}
-
+\end{figure}
+
+\begin{figure}
 \begin{lstlisting}[
@@
 Guild AI is primarily a command line tool. Users type Guild AI
-commands in the form:
-
-{\footnotesize
-\begin{verbatim}
-guild COMMAND [ARG]...
-\end{verbatim}}
+commands in the form: \verb|guild COMMAND [ARG]...|
 
@@
 
-\subsection{History and Lessons Learned}
-
-- Workshops
-- User feedback
-
-\subsection{Packages}
-
-- slim, object-detection, mnist, hello
-
-\subsection{Early Use}
-
-\section{Summary}
+There have been several packaging initiatives that have produced
+reusable models (ref) that fulfill the goals outlined in this
+paper. Specifically, the packages support:
+
+\begin{itemize}
+\item Use without code changes
+\item Reuse by developers who want to new models that leverage
+  packaged functionality
+\item Package maintainer workflow as described in
+  Section~\ref{sec:package-maintainer}
+\item Regression testing as a part of a continuous integration process
+\end{itemize}
 

### 2018-09-28 paper.tex
Wip

@@
   \href{https://pip.pypa.io}{pip} for Python. Such tools excel at
-  creating traditional software packages. However, machine learning
-  applications present unique requirements that call for tool
+  creating traditional software packages. Machine learning
+  applications however present unique requirements that call for tool
   specialization. Guild AI combines the proven effectiveness of
@@
 by myriad techniques, abstractions, and tools. Effective code reuse
-allows developers to leverage prior work in a consistent, reliable
-manner that saves time and improves software quality. In this paper we
+allows developers to leverage prior work in a consistent, reliable way
+that saves time and improves software quality. In this paper we
 consider code reuse in terms of \emph{packaged software} in the
@@
 
-\subsection{Traditional packaged software}
+\subsection{Traditional Packaged Software}
 
@@
 developer, in the case of consuming software libraries or frameworks,
-or she may be an end-user who uses software as a program using a
+or she may be an end-user who uses software as a program with a
 graphical or command line interface. In both cases, packaged software
@@
 \item At a future date \verb|tensorflow| may be similarly uninstalled
-  along with its no-longer-needed required packages.
+  along with its no-longer-used required packages.
 \item The act of installing and uninstalling \verb|tensorflow| should
@@
 
-Such a package management facilities are essential to code reuse at
-the system level. Package managers allow users to consume and manage
-complex software systems with simple commands in a way that maintains
-the integrity of other installed software. They support rapid
-experimentation with new software as users are free to install, use,
-and evaluate packages with the confidence that they can safely remove
-that software later.
+Such package management facilities are essential to code reuse at the
+system level. Package managers allow users to maintain complex
+software systems with simple commands in a way that preserves their
+integrity. They support rapid experimentation with new software as
+users are free to install, use, and evaluate packages with the
+confidence that they can safely remove that software later.
 
@@
 signify that their software will work as advertised if installed using
-the supported tools.
-
-Immense software ecosystems that are enabled by package managers
-include Python, JavaScript, Ruby, Go, and R. The GNU/Linux operating
-system itself is an ecosystem of package management ecosystems
-including packaging schemes from Debian, RedHat, Gentoo, and Arch
+the applicable tools.
+
+Software ecosystems that are enabled by package managers include
+Python, JavaScript, Ruby, Go, and R. The GNU/Linux operating system
+itself is an ecosystem of package management ecosystems including
+packaging schemes from Debian, RedHat, Gentoo, and Arch
 distributions. Package managers are established cornerstones of
@@
 
-\subsection{Code reuse and machine learning models}
+\subsection{Code Reuse and Machine Learning Models}
 
@@
 \emph{trained model} is a model that has learned some representation
-of a system through the process of computer based optimization.
+of a system through an automated process of optimization.
 
@@
 \emph{uninitialized}, \emph{initialized}, \emph{partially trained},
-\emph{fully trained}. Regardless of state, the distinguishing feature
-of machine learning models for our purpose is that they support
-runnable computer operations.
-
-Models---and in particular \emph{trained models}--- are similar to
+\emph{fully trained}, etc. Regardless of state, the distinguishing
+feature of machine learning models for our purpose is that they
+support runnable operations.
+
+Models---and in particular \emph{trained models}---are similar to
 traditional software in that they can be executed to perform
@@
 
-While models may be represented in part by traditional installable
-software---e.g. a TensorFlow program that imperatively defines a model
-graph structure when run---models require more to be construed as
-reusable code: \emph{models must be trainable on novel data}.
-
-The remainder of this paper will outline an approach to package that
-incorporates \emph{model operations} and \emph{run management} as a
-central enabler of code reuse for machine learning models.
+While models may be represented in part by traditional installed
+software---e.g. an imperative TensorFlow program that defines a model
+graph structure when executed---models require more to be construed as
+reusable code: \emph{models must support operations on novel data}. If
+they cannot be applied to novel data---either for training or for
+inference---they cannot be considered reusable software.
+
+The remainder of this paper will outline an approach to package
+management that incorporates \emph{model operations} and \emph{run
+  management} as an enabler of code reuse for machine learning models.
 
@@
 includes source code, examples, documentation, and in some cases
-pretrained models. The \href{Caffe Model Zoo}{Caffe Model Zoo} was one
-of the first model zoos and has inspired several others (ref).
-
-Model zoos encourage code reuse by consolidating related models
-(e.g. based on underlying library implementation or application
-domain) and providing consistent documentation and repeatable methods
-for using the models.
+pretrained models. The Caffe Model Zoo (ref) was one of the first
+model zoos and has inspired several others (ref).
+
+Model zoos encourage code reuse by consolidating related
+models---e.g. based on underlying library implementation or
+application domain---and providing consistent documentation and
+repeatable methods for model use.
 
 Model zoos, however, do not typically provide tools for packaging,
-distributing, and using models, beyond those of publishing source code
+distributing, and using models beyond those of publishing source code
 and documentation (e.g. GitHub, web sites, etc.)
@@
 and using model source code and associated pretrained models. They
-emphasize the use of \emph{transfer learning} where applicable for
-training models on novel datasets.
-
-\subsubsection{Software packages and source code repositories}
+emphasize the use of \emph{transfer learning} for applying pretrained
+models to data from different domains.
+
+\subsubsection{Software Packages and Source Code Repositories}
 
 Models are commonly reused through traditional software distribution
-channels: packages and source code repositories. In both cases, model
-source code is provided along with varying levels of documentation and
-supporting tools. Unlike model zoos and framework packages, there is
-little consistency in quality of code reuse available through these
-channels. Developers are left to their own accord to find and use
-available models.
+channels: \emph{packages} and \emph{source code repositories}. In both
+cases, model source code is provided along with varying levels of
+documentation and supporting tools. Unlike model zoos and framework
+facilities, the level of code reuse available through these channels
+is spotty and inconsistent.
 
@@
 As with model zoos, users can discover Guild AI models, including
-documentation on their use. Guild AI additionally supports
-installation and direct use of models through operations.
+documentation. Guild AI additionally supports installation and direct
+use of models through operations.
 
@@
 discover, install, and use models quickly and easily. Guild AI however
-differs considerably in its implementation. Guild AI does not present
-a language level interface but instead defines a set of conventions
-that are supported through configuration. Guild AI packaging
+differs considerably in its implementation. Guild AI does not use a
+programming interface but instead supports its features by way of
+declared configuration and system level tools. Guild AI packaging
 facilities can be applied to any machine learning model
@@
 
-Guild AI also supports the well established practice of package
-maintenance, where a third party can create usable packages without
-necessarily coordinating with model developers. This is discussed in
-detail in Section \ref{sec:package-maintainer}.
+Guild AI also supports the process of \emph{package maintenance},
+where a third party---a package maintainer---creates usable packages
+without necessarily coordinating with upstream model developers. This
+is discussed in Section \ref{sec:package-maintainer}.
 
@@
 A \emph{project} is a directory that contains model related
-code. Model developers maintain projects for their models. Model users
-maintain projects for the code that works with models, possibly
-training them or otherwise incorporating them into an application.
+code. Model \emph{developers} maintain projects for their
+models. Model \emph{users} maintain projects for their applications,
+which may use models for training, inference, etc.
 
@@
 was generated using the \verb|guild package| command. Guild AI
-packages are no different from standard Python wheel distributions and
-are generated using \verb|setuptools|. However, they contain Guild AI
-specific entry points that effectively publish the models they
-contain.
+packages are generated using \verb|setuptools|. They contain Guild AI
+specific metadata that advertises models they contain.
 
@@
 
-A \emph{model} in Guild AI is a representation of a machine learning
+A Guild AI \emph{model} is a representation of a machine learning
 model that is defined in a Guild file. Models define \emph{operations}
 (Section \ref{sec:operations}) that perform model related tasks such
-as training or evaluating as well as \emph{resources} (Section
-\ref{sec:resources}) that operations may require.
+as training or evaluating as well as \emph{resources} that operations
+may require (Section \ref{sec:resources}).
 
 Models may be defined according to the underlying architecture or
-intended use of the model. Guild AI does not prescribe any formal
-meaning to the term \emph{model} or what operations are supported.
+intended use of the model.
 
@@
 be defined for a model. Model developers are free to name operations
-as they see fit, though Guild AI does encourage naming conventions.
-
-Below are some common operation names:
+as they see fit, though Guild AI does encourage the use of consistent
+naming conventions.
+
+Below are some common operation names.
 
@@
 \item[finetune] finetune a trained model
-\item[evaluate] evaluate a model
-\item[classify] use a trained model to classify inputs
+\item[evaluate] evaluate/test a model
+\item[classify] use a trained model for classification
 \item[compress] compress a trained model (e.g. using quantization,
@@
 
-This list illustrates that model operations can be used to perform a
-host of tasks beyond training and evaluation. In fact, well designed
-models can encompass all of the operations associated with a machine
-learning application development pipeline, from data acquisition and
-preparation to application deployment and monitoring.
+This list illustrates that model operations can be used to perform
+tasks beyond just training and evaluation. Feature rich models can
+encompass all of the operations associated with a machine learning
+development pipeline, from data acquisition and preparation through
+training and optimization to application deployment and monitoring.
 
@@
 A Guild AI \emph{resource} represents a set of source files that can
-be made available as inputs to a model operation. Resources play a key
-role in Guild AI's ability to effective use models. Resources can be
-used to resolve project files, download files from URLs, unpack
-archives, and reference files generated by other operation.
-
-Listing~\ref{lst:resource} illustrates a resource definition for a
+be made available as inputs to a model operation. Resources play an
+important role in Guild AI's ability to effective use
+models. Resources can be used to resolve project files, download files
+from URLs, unpack archives, and reference files generated by other
+operation.
+
+Listing~\ref{lst:resource} contains a resource definition for a
 model. The resource \verb|idx-data| defines four source files that
@@
 
-Runs are described in detail in Section \ref{sec:runs}.
+Runs are further described in Section \ref{sec:runs}.
 
@@
 
-A \emph{run directory} is a directory used for a run. During a run
-operation, the run directory is the system current working
-directory. Operations should write run artifacts within the current
-working directory to ensure that they are associated with the run.
+A \emph{run directory} is a directory used for a run. When an
+operation is run, the run directory is used as the operating system
+process working directory. Operations should write run artifacts
+within the working directory to ensure they are associated with the
+run.
 
 By default, Guild AI generates a new directory for each run and
-creates links to required resource sources within that directory. Once
-the directory is prepared, Guild AI starts the run operating system
-process, which then may access sources within the current working
-directory.
-
-Users may optionally specify an alternative run directory for a
-run. This is commonly used by model developers during the process of
-implementing model operation.s
+creates links to required sources within that directory. Once the
+directory is prepared, Guild AI starts the run operating system
+process, which may read sources within the run directory.
 
@@
 by running operations in specific order. Worflows are not currently
-formal constructs in Guild AI but are referenced by convention or
-documented usage.
+formal constructs in Guild AI but are used by convention and may be
+implemented by other programs.
 
@@
 
-Given a Guild file with a package definition, develolpers can use
+Given a Guild file with a package definition, developers can use
 Guild AI to generate a Python wheel distribution, which in turn can be
@@
 Project models are defined in a project Guild file---i.e. a file named
-\verb|guild.yml| that resides in the top level of a projet
+\verb|guild.yml| that resides in the top level of a project
 directory. Users may run operations on project models by running them
-from within the project directory or by refering the project directory
+from within the project directory or by referring the project directory
 in the operation specified for the \verb|run| command.
@@
 model documentation for developers and gives users a consistent
-interface for discovering model capabilities and intructions for using
+interface for discovering model capabilities and instructions for using
 them.
@@
 \emph{operations}. Operations generate \emph{artifacts} that can be
-used in subsquent operations or as final outputs in an application
+used in subsequent operations or as final outputs in an application
 development workflow.
@@
 alternative directory for the run. This is helpful when the developer
-doesn't want to generate new runs for early stage opertion
+doesn't want to generate new runs for early stage operation
 development.
@@
 wants to incorporate into a formalized model definition. As with the
-role of \emph{packger} (Section~\ref{sec:package-maintainer}), a
+role of \emph{packager} (Section~\ref{sec:package-maintainer}), a
 developer may even be required to work with upstream sources she
@@
 In cases where a developer cannot modify upstream sources or chooses
-not to (e.g. to simplify ongoing mainteance) he may choose to patch
+not to (e.g. to simplify ongoing maintenance) he may choose to patch
 model sources for use in a model. Guild AI supports two methods of
@@
 
-Configuation inheritance can be applied across Guild files---e.g. to
+Configuration inheritance can be applied across Guild files---e.g. to
 configuration defined in packages or other projects. This is useful
@@
 \emph{Python main module reuse}. Main modules---i.e. the modules
-referenced in an opertion \verb|main| specification---may reside in
+referenced in an operation \verb|main| specification---may reside in
 any installed Python package. To reuse the main module, a developer
@@
 
-Listing~\ref{lst:tflite_convert} illustates the use of the TensorFlow
-module \verb|tflite_convert| to generte a TF Lite file for an
+Listing~\ref{lst:tflite_convert} illustrates the use of the TensorFlow
+module \verb|tflite_convert| to generate a TF Lite file for an
 operation.
@@
 help---ensuring that what the user sees when she runs
-\verb|guild help| is what the developer intendes---and another that
+\verb|guild help| is what the developer intends---and another that
 exercises model operations and checks results.

### 2018-09-28 paper.tex
Wip

@@
 \item[packager] person neither using nor developing a model but who
-  packages models created by developers for use by users
+  packages models created by developers for users
 \end{description}
@@
 feedback from expert users, improved reputation, a sense of
-contribution, or her colleagues may simply expect that work be
+contribution, or her colleagues may simply expect that her work be
 documented and easy to use.
 
-While documenting the steps needed to use a model is undoubtedly
-helpful, the process is still burdensome for both the developer and
-her users. Guild AI can be used to simultaneously document model use
-but also directly support its use through model operations.
-
-Consider these instructions for model use, which might be documented
-for a project:
+While documenting a model is undoubtedly helpful, the process can be
+burdensome for the developer. Similarly, following documented steps
+can be burdensome for users. Guild AI can be used to simultaneously
+document model features and support model usage through operations.
+
+Consider these instructions for model use:
 
@@
 \item Install required packages
-\item Download the raw data
-\item Prepare the raw data for training
+\item Download the data
+\item Prepare the data for training
 \item Train the model
@@
 While these steps provide invaluable information, they still rely on
-the user to carefully execute them and troubleshoot issues as they
-arise. The process takes time and is subject to error at any step.
+the user to carefully execute them and troubleshoot issues. The
+process takes time and is subject to error at any step.
 
@@
 might be used to codify the steps as model operations.
+
+The operations can be run using the Guild AI command line interface as
+follows:
+
+{\footnotesize
+\begin{verbatim}
+ $ guild run prepare-data
+ $ guild run train
+ $ guild run export-model
+\end{verbatim}}
+
+Guild AI additionally provides model help, detailing available
+operations, supported flags, and operation dependencies.
+
+A user can get help for the model by running:
+
+{\footnotesize
+\begin{verbatim}
+ $ guild help
+\end{verbatim}}
+
+Documentation is automatically generated from the model description,
+making Guild AI models self documenting.
+
+The developer can chose to distribute her model as a
+project---e.g. making it available as a GitHub repository---or she may
+package the model and deploy it as an installable Python wheel
+distribution.
 
@@
       Prepare data for training
-    main: prepare_data
-    requires: raw-data
+    main: prepare
+    requires: data
   train:
-    description: Train model
+    description: Train the model
     main: train
@@
     description:
-      Export model for deployment
+      Export the model for deployment
     main: export_model
@@
 resources:
-  raw-data:
-    description: Raw data for training
+  data:
+    description: Data for training
     sources:
-      - url: http://mydata.com/raw.tgz
+      - url: http://my.co/data.tgz
   prepare-data:
@@
 
-The operations can be run using the Guild AI command line interface as
-follows:
-
-{\footnotesize
-\begin{verbatim}
- $ guild run prepare-data
- $ guild run train
- $ guild run export-model
-\end{verbatim}}
-
-Furthermore, Guild AI provides model help, detailing available
-operations, supported flags, and operation dependencies.
-
-A user can get help for the model by running:
-
-{\footnotesize
-\begin{verbatim}
- $ guild help
-\end{verbatim}}
-
-Documentation is automatically generated from the model description,
-making Guild AI models self documenting.
-
-The developer can chose to distribute her model as a
-project---e.g. making it available as a GitHub repository. She may
-alternatively package the model and deploy as an installable Python
-wheel distribution artifact.
-
 \subsection{Use a Published Model}
@@
 
-The flip side of the use case outline in
-Section~\ref{sec:publish-model} is that of the \emph{user}. A user is
-interesting in taking the work of a model developer and applying it,
-either by adapting her model to a new application or by integrating
-it as into another project.
-
-Users commonly rely on thorough documentation to effectively use
-models. If a project is under documented or otherwise hard to work
-with, it may not be used. This is a lost opportunity for both user and
-developer that hinders adoption and model improvement.
-
-As described in Section~\ref{sec:publish-model}, a published model is
-simple to use. From the standpoint of the user, the model can be used
-either by cloning the project repository---e.g. as in the case of
-GitHub published models---or install the model as a Python
-package. Assuming the project was published as a package named
-\verb|sample-project|, the user might run these commands to use the
-model:
-
-\setlength{\parindent}{1em}
+The flip side of the use case outlined in
+Section~\ref{sec:publish-model} is from the \emph{user} point of
+view. A user is interested in taking the work of a model developer and
+applying it, either by adapting the model to a new application or by
+integrating it as-is into a project.
+
+Users commonly rely on documentation to effectively use models. If a
+project is poorly documented or otherwise hard to work with, the user
+may choose not to use it. This would be a lost opportunity for both
+user and developer and would hinder model adoption and improvement.
+
+As described in Section~\ref{sec:publish-model}, a published model can
+be used by running its operations. From the standpoint of the user,
+the model can be consumed either by cloning the project
+repository---e.g. as in the case of GitHub published models---or by
+installing the model as a Python package. If, for example, the project
+was published as the package \verb|sample-project|, a could user run
+the commands below to quickly make use of its features.
+
+\setlength{\parindent}{0.67em}
 
@@
 
-This illustrates the usefulness of packaging models for
+This example highlights the usefulness of packaging models for
 reuse. Packaged models in this case consist of more than the
-underlying model code---they include additional information that makes
-them trivial to use relative to traditional forms of model reuse.
+underlying model code---they include essential configuration that lets
+Guild AI \emph{execute model operations}.
 
@@
 Complex software ecosystems such as GNU/Linux have formalized the role
-of a software \emph{packager} (or \emph{package maintainer}). The goal
+of a software \emph{packager}---or \emph{package maintainer}. The goal
 of a packager is to improve the value of a software distribution by
-creating high quality software packages that users find
-useful. Packers are often independent of the upstream software
-projects they package, serving as intermediaries between the software
+creating high quality, useful packages that are easy to install and
+use. Packagers are often independent of the upstream software projects
+they package, serving as intermediaries between the software
 developers and distribution users.
@@
 Consider a case where a model developer is overloaded with research
-tasks and doesn't have time to provide documentation for using her
-models or publishing them for use as described in
-Section~\ref{sec:publish-model}. An independent \emph{packager} may
-step up to create a package instead.
+tasks and doesn't have time to create model documentation, much less
+publish models as described in Section~\ref{sec:publish-model}. An
+independent \emph{packager} may step up to create a package instead.
 
 A packager must assume that upstream sources are available \emph{as
-  is} and he cannot expect developers to fix bugs or add new features
-(though he may certainly ask and hope). Packagers therefore must be
-prepared to \emph{patch} model code as needed to get it to work as
-expected.
+  is} and cannot expect developers to fix bugs or add new
+features---though he may certainly submit requests and remain
+hopeful. Packagers therefore must be prepared to \emph{patch} model
+code as needed to get it to work as expected.
 
 Guild AI provides various means of patching model source to support
-packagers in this role.
+packagers in this role. Section~\ref{sec:patching} describes patching
+methods.
 
@@
 
-Within a typical organization structure, the roles map as follows:
+Within a typical organization structure, the may roles map as follows:
 
@@
 
-Of course this is a rough mapping and not all organizations share this
+Of course this is a rough mapping and not all organizations use this
 structure. Whatever the job titles and division of labor, Guild AI
 supports the three facets of collaboration: model development, model
-use, and intermediation between those two points in the interest of
-freeing up developer time and resources to focus on pure model
-development.
+use, and intermediation between developer and user as needed to
+improve usability without unduly burdening developers.
 
@@
 
-The final use case discussed involves managing tracking run artifacts.
-During both model development and use, it's useful to formally manage
-the artifacts both generated and consumed by model operation. This is
-similar to source code revision control, where developers can move
-backward and forward in time to view their work. In the case of Guild
-AI, the revisions are the results of data preparation, training
-experiments, model optimizations---anything that might be generated by
-an operation.
-
-Section~\ref{sec:runs} provides more details about Guild AI run
-management.
+The final use case discussed involves managing runs and tracking run
+artifacts. During both model development and use, it's helpful to
+formally manage run artifacts both generated and consumed by model
+operation. This is similar to source code revision control, where
+developers can move backward and forward in time to view their
+work. In the case of Guild AI, the revisions are the results of data
+preparation, training experiments, model optimizations---anything that
+might be generated by an operation.
+
+Section~\ref{sec:runs} describes Guild AI run management.
 
@@
 
-Packaged models are models that have been bundles with supporting code
+Packaged models are models that have been bundled with supporting code
 and metadata into a Python wheel distribution. To generate a package,
@@
 
-Given a Guild file with a package definition, developers can use
-Guild AI to generate a Python wheel distribution, which in turn can be
-used by users to install package models. Developers can also upload
-packages to PyPI to make the package available for search and
-installation.
+Given a Guild file with a package definition, developers can generate
+a Python wheel distribution, which in turn can be used to install
+package models. Developers can additionally upload packages to PyPI,
+making them available to discover and install.
 
@@
 
-Alternatively, a user may use pip:
+Or alternatively use pip:
 
@@
 
-Package models are convenient for using models and their related
-functionality when a user doesn't need to modify the model source
-code. To use models and also have the option of modifying their source
-code, a user should use project models (Section
-\ref{sec:project-models}).
+Package models are convenient for using models when a user doesn't
+need to modify the model source code. To use models and also have the
+option of modifying model source code, a user should use project
+models (Section \ref{sec:project-models}).
 
@@
 directory. Users may run operations on project models by running them
-from within the project directory or by referring the project directory
-in the operation specified for the \verb|run| command.
-
-Project models are used by users or developers who expect to modify
-project files.
+from within the project directory or by referring the project
+directory in the operation specified for the \verb|guild run| command.
 
@@
 feature enabling model use in Guild AI. Without formally defining
-these, users are left to their own to infer model capabilities from
-available documentation and source code.
+these, users must infer model capabilities from documentation and
+source code.
 
@@
 
-A user may use the \verb|guild help| command to get details about a
+A user may run the \verb|guild help| command to show details about a
 model, its operations, operation flags, and resource
@@
 model documentation for developers and gives users a consistent
-interface for discovering model capabilities and instructions for using
-them.
+interface for discovering model capabilities and the commands for
+using them.
 
@@
 operation is an action that can be performed on a model. Operations
-both \emph{define and implement} model capabilities. The act of using
-a model is the process of running operation.
+both \emph{define and implement} model capabilities. The process of
+using a model is the process of running operation.
 
@@
 operating process and a Guild AI managed file system artifact that
-contains run details including generated output.
+contains run details and generated output.
 
@@
 
-Refer to Section~\ref{sec:runs} for information about managing runs.
+Section~\ref{sec:runs} describes how runs are managed.
 
@@
 Guild AI also provides various methods for visualizing runs. Guild
-View is an application that is provided with Guild AI that launches a
-web application that can be used to view run details, including run
-files.
-
-Guild AI also integrates TensorBoard (ref) as a visualization tool,
-which can be used to view TensorFlow event logs that are generated by
-model operations.\footnote{Operations must explicitly write TensorFlow
-  event logs during a run to support TensorBoard visualization.}
+View is an application provided with Guild AI that displays run
+details including run files. Guild AI integrates TensorBoard (ref) as
+a visualization tool for viewing TensorFlow event logs generated by
+model operations.\footnote{Not all operations generate TensorFlow
+  event logs---these must be explicitly written during a run by the
+  operation.}
 
@@
 example, a TensorFlow checkpoint generated by a \verb|train| operation
-may be used as input to an \verb|export-and-freeze| operation, which
-in turn generates a frozen inference graph. This process is automatic
-and part of Guild AI's resource resolution process.
+may be used as input to an \verb|export-and-freeze| operation. The
+process of resolving required operation sources is automatic and part
+of Guild AI's run support.
 
@@
 with a run using the \verb|guild runs info| command with the
-\verb|-ff| option. With these path, the user may copy the files or
+\verb|-ff| option. Using their paths, a user can copy desired files or
 link to them as needed.
@@
 Runs may also be \emph{exported} to a location using the
-\verb|guild export| command. Exported runs are copied (or moved, if
-the \verb|--move| option is specified) to a specified file system
-directory. This can be used to create backups or to transfer runs to
-another location.
+\verb|guild export| command. Exported runs are copied---or moved, if
+specified---to a specified file system directory. This can be used to
+create backups or to transfer runs to another location.
 
@@
 \subsection{Patching}
+\label{sec:patching}
 

### 2018-09-28 paper.tex
Wip

@@
   aboveskip=12pt,
-  basicstyle=\footnotesize\ttfamily,
+  belowskip=0pt,
+  basicstyle=\fontsize{8.5pt}{8.5pt}\ttfamily,
   breaklines=true,
@@
 \setlist[description]{
-  itemsep=4pt,
+  itemsep=0pt,
+  topsep=0pt,
   labelindent=1em,
   leftmargin=1em,
-  topsep=4pt,
 }
@@
 \setlist[enumerate]{
-  itemsep=4pt,
-  topsep=4pt,
+  itemsep=0pt,
+  topsep=0pt,
 }
@@
 \setlist[itemize]{
-  itemsep=4pt,
-  topsep=4pt,
+  itemsep=0pt,
+  topsep=0pt,
   labelindent=1em,
@@
   management strategies are central to successful software
-  ecosystems. Examples include \href{https://www.npmjs.com/}{npm} for
-  JavaScript, \href{https://wiki.debian.org/Apt}{APT} for Debian, and
-  \href{https://pip.pypa.io}{pip} for Python. Such tools excel at
-  creating traditional software packages. Machine learning
+  ecosystems. Examples include npm for JavaScript \cite{npm}, APT for
+  Debian \cite{apt}, and pip for Python \cite{pip}. Such tools excel
+  at creating traditional software packages. Machine learning
   applications however present unique requirements that call for tool
@@
 By running this command, a user is using a \emph{package manager}---in
-this case the program \verb|pip|---to install a package named
+this case the program \texttt|pip|---to install a package named
 \verb|tensorflow|. With this innocuous command, the user implicitly expects
@@
 
+\iffalse
 Package managers promote healthy software ecosystems by facilitating
@@
 software reuse across languages and operating systems.
+\fi
 
@@
 
+\iffalse
 While models may be represented in part by traditional installed
@@
 inference---they cannot be considered reusable software.
+\fi
 
@@
 
+\iffalse
 Guild AI provides various means of patching model source to support
@@
 methods.
+\fi
 
@@
 
+\iffalse
 \subsection{Manage Run Artifacts}
@@
 Section~\ref{sec:runs} describes Guild AI run management.
+\fi
 
@@
 The discussion of using models to this point has not mentioned
-\emph{environments} as environment are optional for using Guild
-AI. However, environments are useful for isolating installed packages
+\emph{environments}---environment are optional for using Guild
+AI. Environments are useful, however, for isolating installed packages
 and runs on a system.
@@
 
-Environments are useful isolating project level work. It's not uncommon
-to have separate environments for each project.
+Environments are useful isolating project level work. It is common to
+have a separate environment for each project or work stream.
 
@@
   resolved dependencies
-\item Output generated by the run---specifically the operating system
-  process standard output and standard error
+\item Output generated by the run---specifically the process standard
+  output and standard error
 \item Files used by the operation (resolved resource sources)
@@
 
-Runs are started using the \verb|guild run| command and referencing a
+Runs are started using the \verb|guild run| command, referencing a
 model operation. Operations may be run with additional flag values
-provided on the command line in the format \verb|NAME=VALUE|.
+provided in the format \verb|NAME=VALUE|.
 
@@
 As discussed above, published models---deployed from installed
-packages or as projects---can be used by running model
+packages or as projects---are used by running
 \emph{operations}. Operations generate \emph{artifacts} that can be
-used in subsequent operations or as final outputs in an application
-development workflow.
-
-In this section we discuss how such models are created using Guild AI.
+used in subsequent operations or used as final outputs in an
+application development workflow.
+
+In this section we discuss how models are created using Guild AI.
 
@@
 
-In many cases, this is simply a matter of selecting a model name and
-creating a \verb|train| operation. Listing~\ref{lst:pet-stub}
+In some cases, this may simply be a matter of selecting a model name
+and creating a \verb|train| operation. Listing~\ref{lst:pet-stub}
 illustrates a straightforward pet classifier.
@@
 With even a simple stub, a developer can formalize the model and what
-it does. This stage clarifies the model's user interface before the
+it does. This stage clarifies the model interface before the
 functionality is implemented.
 
-With a basic skeleton in place, the developer can implement model
-operations. In the case of the pet classifier
-(Listing~\ref{lst:pet-stub}) this means implementing training support
-in a file named \verb|train.py| that resides in the project directory.
-
-Operations can be developed and tested early on using Guild AI. Each
-time \verb|guild run| is used to test an operation, Guild AI generates
-a distinct, trackable run. Runs may be compared over time to help
-answer questions or resolve issues.
+With a basic skeleton in place, the developer can \emph{implement}
+model operations. In the case of the pet classifier in
+Listing~\ref{lst:pet-stub} this means implementing train support in a
+file named \verb|train.py| that resides in the project directory.
+
+Operations can be developed and tested early using Guild AI. Each time
+\verb|guild run| is used to test an operation, Guild AI generates a
+distinct, tracked run. Runs may be compared over time to help answer
+questions or resolve issues.
 
@@
 
-The first is the use the \verb|--run-dir| option
-to the \verb|guild run| command. This option may be used to specify an
-alternative directory for the run. This is helpful when the developer
-doesn't want to generate new runs for early stage operation
-development.
-
-The second mechanism is the use of the \verb|--stage| option to the
+The first mechanism is the use of \verb|--run-dir| with the
+\verb|guild run| command. This option specifies an alternative
+directory for the run. This is helpful when the developer doesn't want
+to generate new runs during the development process.
+
+The second mechanism is the use of \verb|--stage| with the
 \verb|guild run| command. This option may be used to stage a run in an
@@
 
+\iffalse
 The developer can continue to evolve the model operations as needed to
@@
 the Guild file.
+\fi
 
@@
 role of \emph{packager} (Section~\ref{sec:package-maintainer}), a
-developer may even be required to work with upstream sources she
-cannot easily change. Guild AI provides a number of features that
-support the adaptation of existing model code into usable models.
+developer may be required to work with upstream sources she cannot
+easily change. Guild AI provides a number of features that support the
+adaptation of existing model code into usable models.
 
@@
 Python script to incorporate it into an operation. In cases where a
-script doesn't already exist---for example, the model code is in a
-Jupyter Notebook and not readily usable---the developer should create
-a new script that contains the applicable model code and use it for an
-operation.
+script doesn't exist---for example, the model code is in a Jupyter
+Notebook---the developer must create a new script that contains the
+applicable model code and specify it for the operation.
 
@@
 command \verb|python -m train --epochs 100|. In this way developers
-can parameterize scripts via operation flags.\footnote{It is standard
-  practice to use Python's argparse module to support named command
-  line options following the getopt convention (ref) in a Python
-  script.}
-
+can parameterize scripts using operation flags.\footnote{It is
+  standard practice to use Python's argparse module to support named
+  command line options following the getopt convention (ref).}
+
+\iffalse
 If a flag name doesn't correspond to the option name expected
@@
 the \verb|arg-name| attribute.
+\fi
 
@@
 
-Guild files may contain \verb|config| section that contain arbitrary
-configuration, which can be inherited by
-models. Listing~\ref{lst:inheritance} defines two models, each
-inheriting the properties of shared config. The shared config
-\verb|model-base| defines the common model operations and uses
-\emph{parameters} to define a model name and default learning rate.
+Guild files may contain \verb|config| sections that that can be
+inherited by models definitions. Listing~\ref{lst:inheritance}
+contains two models, each inheriting the properties of shared
+configuration. The shared config \verb|model-base| defines the common
+model operations and uses \emph{parameters} to define a model name and
+default learning rate.
 
@@
 
+\iffalse
 \subsubsection{Configuration Includes}
@@
 
+\fi
+
 \subsubsection{Reusing Python Main Modules}
 
-The final method of model definition reuse described is that of
+The final method of model definition reuse discussed is that of
 \emph{Python main module reuse}. Main modules---i.e. the modules
@@
 Listing~\ref{lst:deploy} illustrates how such a facility could be
-easily incorporated into a model to enable deployments. In the
-example, the model is defined in a package that requires the
-\verb|server-utils| package, which will be automatically installed by
-the command \verb|guild install classifiers|.
+incorporated into a model to enable deployments. In the example, the
+model is defined in a package that requires the \verb|server-utils|
+package, which will be automatically installed by the command
+\verb|guild install classifiers|.
 
@@
 
-Tests can be run using the \verb|guild test| command.
-
+Tests are run using the \verb|guild test| command.
+
+\iffalse
 Tests may be run on an ad hoc basis or as a continuous integration
 release process.
-
-\subsection{Packaging}
-
-Our final point of discussion on the topic of model development is
-\emph{packaging}. Packaging consists of generating a Python wheel
-distribution that contains the Guild file and all supporting project
-code. The generated wheel distribution may be distributed internally
-within an organization or published to PyPI.
-
-Packages that are published to PyPI can be installed using the command
-\verb|guild install| or using pip.
-
-Packages are convenient for installing
-
+\fi
+
+\iffalse
 \section{Implementation}
@@
 Guild AI is written in the Python programming language. It makes use
-of a number of excellent open source libraries, many of which are
+of a number of excellent open source libraries, some of which are
 listed below.
@@
 
-Guild AI makes use of the Click Python library (ref) to implement its
-core command line processing support.
+Guild AI makes use of the Click Python library \cite{click} to
+implement its core command line processing support.
 
@@
 end and Werkzeug (ref) for the HTTP API back end.
+\fi
 

### 2018-10-02 paper.tex
Submitted

@@
   at creating traditional software packages. Machine learning
-  applications however present unique requirements that call for tool
-  specialization. Guild AI combines the proven effectiveness of
+  applications, however, present unique requirements that call for
+  tool specialization. Guild AI combines the proven effectiveness of
   package managers with novel features to enable machine learning
@@
 easily installed and used by \emph{users}. A user is a consumer of
-software, rather than a producer or developer. A user may be software
-developer, in the case of consuming software libraries or frameworks,
-or she may be an end-user who uses software as a program with a
-graphical or command line interface. In both cases, packaged software
-may be provided in units that the user can install and start using
-quickly and reliably.
+software, rather than a producer or developer. A user may be a
+software developer, in the case of consuming software libraries or
+frameworks, or she may be an end-user who uses software as a program
+with a graphical or command line interface. In both cases, packaged
+software may be provided in units that the user can install and begin
+using quickly and reliably.
 
@@
 By running this command, a user is using a \emph{package manager}---in
-this case the program \texttt|pip|---to install a package named
+this case the program \verb|pip|---to install a package named
 \verb|tensorflow|. With this innocuous command, the user implicitly expects
@@
   also be installed.
-\item Installed software should work as expected on the target system.
+\item Installed software will work as expected on the target system.
 \item At a future date \verb|tensorflow| may be similarly uninstalled
@@
   not break or otherwise destabilize other installed software on the
-  target system.
+  system.
 \end{itemize}
@@
 integrity. They support rapid experimentation with new software as
-users are free to install, use, and evaluate packages with the
-confidence that they can safely remove that software later.
+users are free to install and evaluate packages with the confidence
+that they can safely remove that software later.
 
@@
 have different contexts. In the most general context, models are
-mathematical concepts or language that represents a system (ref). In
-the context of machine learning, models may be represented by computer
-source code, either explicitly as declared structures, or implicitly
-by way of executable instructions that perform model related tasks. A
+mathematical concepts or language that represents a system. In the
+context of machine learning, models may be represented by source code,
+either explicitly as declared structures, or implicitly by way of
+executable instructions that perform model related tasks. A
 \emph{trained model} is a model that has learned some representation
@@
 
-\subsubsection{Model zoos}
+\subsubsection{Model Zoos}
 
@@
 includes source code, examples, documentation, and in some cases
-pretrained models. The Caffe Model Zoo (ref) was one of the first
-model zoos and has inspired several others (ref).
+pretrained models. The Caffe Model Zoo \cite{caffezoo} was one of the
+first model zoos and has inspired several others \cite{tfzoo,mxzoo}.
 
@@
 
-\href{https://www.tensorflow.org/hub/}{TensorFlow Hub modules} and
-\href{https://keras.io/applications/}{Keras Applications} are examples
-of framework level facilities that provide a higher degree of model
-reuse vis-\'a-vis model zoos. Both TensorFlow Hub modules and Keras
-application support tools and patterns for packaging, distributing,
-and using model source code and associated pretrained models. They
-emphasize the use of \emph{transfer learning} for applying pretrained
-models to data from different domains.
+TensorFlow Hub modules \cite{tfhub} and Keras Applications
+\cite{kerasapps} are examples of framework level facilities that
+provide a higher degree of model reuse vis-\'a-vis model zoos. Both
+TensorFlow Hub modules and Keras application support tools and
+patterns for packaging, distributing, and using model source code and
+associated pretrained models. They emphasize the use of \emph{transfer
+  learning} for applying pretrained models to data from different
+domains.
 
@@
 
-A Guild AI \emph{package} is a Python wheel distribution (ref) that
-was generated using the \verb|guild package| command. Guild AI
-packages are generated using \verb|setuptools|. They contain Guild AI
-specific metadata that advertises models they contain.
+A Guild AI \emph{package} is a Python wheel distribution \cite{wheels}
+that was generated using the \verb|guild package| command. They
+contain Guild AI specific metadata that advertises models they
+contain.
 
@@
 be made available as inputs to a model operation. Resources play an
-important role in Guild AI's ability to effective use
+important role in Guild AI's ability to effectively use
 models. Resources can be used to resolve project files, download files
@@
 A \emph{run directory} is a directory used for a run. When an
-operation is run, the run directory is used as the operating system
-process working directory. Operations should write run artifacts
-within the working directory to ensure they are associated with the
-run.
+operation is run, the run directory is used as the process working
+directory. Operations should write run artifacts within the working
+directory to ensure they are associated with the run.
 
@@
 creates links to required sources within that directory. Once the
-directory is prepared, Guild AI starts the run operating system
+directory is prepared with required sources, Guild AI starts the run
 process, which may read sources within the run directory.
@@
 environments used for installing and using models. Guild AI supports
-environments created using
-\href{https://virtualenv.pypa.io}{\emph{virtualenv}}.
+environments created using {\emph{virtualenv} \cite{venv}.
 
@@
 model, its operations, operation flags, and resource
-dependencies. This is similar to the \emph{man} facility (ref) on many
+dependencies. This is similar to the \emph{man} facility on many
 systems.
@@
 View is an application provided with Guild AI that displays run
-details including run files. Guild AI integrates TensorBoard (ref) as
-a visualization tool for viewing TensorFlow event logs generated by
+details including run files. Guild AI integrates TensorBoard \cite{tb}
+as a visualization tool for viewing TensorFlow event logs generated by
 model operations.\footnote{Not all operations generate TensorFlow
@@
 \verb|guild export| command. Exported runs are copied---or moved, if
-specified---to a specified file system directory. This can be used to
+specified---to a different file system directory. This can be used to
 create backups or to transfer runs to another location.
@@
 
-When running Guild AI operations in an activated environment, the
+When running Guild AI commands in an activated environment, the
 following are environment specific:
@@
 \begin{itemize}
-\item Installed packages and therefore installed models
+\item Installed packages and models
 \item Runs
@@
 One or more runs may be deleted using the \verb|guild runs rm|
-command. Runs may be deleted using status, operation, or label.
+command. Runs may be deleted by status, operation, or label.
 
@@
   standard practice to use Python's argparse module to support named
-  command line options following the getopt convention (ref).}
+  command line options following the getopt convention \cite{getopt}.}
 
@@
 
-The second method is to wrap upstream scripts and monkey patch (ref)
-the Python environment as needed to change behavior. An example of
-this can be found in the \verb|gpkg.slim| package, which patches the
+The second method is to wrap upstream scripts and monkey patch the
+Python environment as needed to change behavior. An example of this
+can be found in the \verb|gpkg.slim| package, which patches the
 TensorFlow \verb|slim.losses.softmax_cross_entropy| module to add
@@
 \begin{lstlisting}[
-    caption=Quickly enabling model deploy,
+    caption=Enabling model deploy,
     label={lst:deploy}]
@@
 
-Guild AI supports YAML (ref) as its configuration language for both
+Guild AI supports YAML \cite{yaml} as its configuration language for both
 Guild files and user configuration. It uses the PyYAML Python library
@@
 
-Guild AI is freely available under the Apache 2.0 open source
+Guild AI is freely available under the Apache 2.0 \cite{guild} open source
 license. It has been under active development for the last two years
@@
 There have been several packaging initiatives that have produced
-reusable models (ref) that fulfill the goals outlined in this
-paper. Specifically, the packages support:
+reusable models \cite{pkg} that fulfill the goals outlined in this
+paper:
 
